### 2020-11-14 guide/guide.tex
Add first preview of guide.

\documentclass[12pt, letterpaper, fleqn, notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{newtxtext}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,amsthm}

\title{Running RL algorithms on the aquarium environment to find unexpected biological insights}
\date{\today}
\author{Daniel Ratke}

\begin{document}
\maketitle

\section{Introduction}

The scope of this document is fluid. For now, this is a quick guide on the
aquarium environment to get students up and running in a small amount of time.
Later, short summaries of the research conducted using this environment may be
added.

The following section shortly describes the premise of the environment and
important details such as the observation space and the action space.

Authors of the environment include Carsten Hahn, Fabian Ritz and Thomy Phan.

\section{The Environment}

The main purpose of the aquarium environment is to simulate an aquarium full of
a variable amount of fishes and sharks. Movement is relatively realistic and
may be based on realistic rules such as the Boids framework.

Before the simulation starts, the number of fishes including their respective
strategies and the number of sharks is defined. There are a multitude of
further settings such as the number of walls or fishes that can be observed.
Even the behavior of the walls themselves may be adapted, for instance to
define the world as a torus.

A major point of the environment is exchangeability --- there is a base animal
class from which both fishes and sharks inherit, and each fish may have a
different strategy. Same can be said about the sharks.

\begin{figure}
  \includegraphics[width=\linewidth]{demo.png}
  \caption{The aquarium. Orange circle is a shark, green circles are fishes.}\label{fig:demo}
\end{figure}

Figure~\ref{fig:demo} shows an examplary simulation.

\subsection{Observation Space}

% TODO: Partial observability.

\subsection{Action Space}

\end{document}

### 2020-11-14 guide/compile.sh

@@ -1,0 +1,1 @@
+pdflatex guide.tex

### 2020-11-15 old/projekt_parser/parser.py
Move convenience, projekt_parser, remote to old.

@@ -46,8 +46,3 @@ class SafeConfigParser(ConfigParser):
         if any([(c in literal) for c in self.harmful_calls]):
             raise ValueError("Harmful literal found in config!")
         return literal
-
-
-
-
-

### 2020-11-15 old/main.py
Move some more code to old.

@@ -1,0 +1,14 @@
+import os
+import sys
+from framework.buildingblocks import Experiment
+os.chdir(os.path.abspath(os.path.dirname(__file__)))
+
+if __name__ == '__main__':
+    config_file = sys.argv[1]
+    e = Experiment(config_file)
+    e.start_phase_one()
+    e.start_phase_two()
+    e.flag_done()
+
+
+

### 2020-11-15 plot/show_stats.py

@@ -254,7 +254,3 @@ if __name__ == '__main__':
         which_file = int(sys.argv[3])
         mode_keys(which_experiment, which_file)
         exit(0)
-
-
-
-

### 2020-11-15 main.py
Add new (WIP) main.py using OpenAI baselines (PPO1).

@@ -1,14 +1,58 @@
-import os
-import sys
-from framework.buildingblocks import Experiment
-os.chdir(os.path.abspath(os.path.dirname(__file__)))
+#!/usr/bin/env python3
+from baselines import logger
+from baselines.common import tf_util as U
+from baselines.ppo1 import mlp_policy, pposgd_simple
+from env.aquarium import Aquarium
+
+
+class Experiment:
+    def __init__(self):
+        self.num_timesteps = 10000
+
+        self.env = Aquarium(
+            nr_sharks=1,
+            nr_fishes=10,
+            observable_sharks=3,
+            observable_fishes=3,
+            observable_walls=2,
+            size=30,
+            max_steps=500,
+            max_fish=10,
+            max_sharks=1,
+            torus=False,
+            fish_collision=True,
+            lock_screen=True,
+            seed=42
+        )
+        self.env.select_fish_types(
+            RandomFish=0,
+            TurnAwayFish=10,
+            BoidFish=0
+        )
+        self.env.select_shark_types(Shark_Agents=1)
+
+    def train(self):
+        logger.configure()
+
+        U.make_session(num_cpu=1).__enter__()
+
+        def policy_fn(name, ob_space, ac_space):
+            return mlp_policy.MlpPolicy(
+                name=name,
+                ob_space=ob_space,
+                ac_space=ac_space,
+                hid_size=64,
+                num_hid_layers=2
+            )
+
+        pposgd_simple.learn(
+            self.env, policy_fn, max_timesteps=self.num_timesteps,
+            timesteps_per_actorbatch=2048, clip_param=0.2, entcoeff=0.0,
+            optim_epochs=10, optim_stepsize=3e-4, optim_batchsize=64,
+            gamma=0.99, lam=0.95, schedule='linear'
+        )
+        self.env.close()
+
 
 if __name__ == '__main__':
-    config_file = sys.argv[1]
-    e = Experiment(config_file)
-    e.start_phase_one()
-    e.start_phase_two()
-    e.flag_done()
-
-
-
+    Experiment().train()

### 2020-11-15 guide/guide.tex
Add notes about observation space, action space and reward to guide. Also add bibliography.

@@
 added.
-
+%
 The following section shortly describes the premise of the environment and
 important details such as the observation space and the action space.
-
+%
 Authors of the environment include Carsten Hahn, Fabian Ritz and Thomy Phan.
@@
 may be based on realistic rules such as the Boids framework.
-
+%
 Before the simulation starts, the number of fishes including their respective
@@
 define the world as a torus.
+%
+A major architectural point of the environment is exchangeability --- there is
+a base animal class from which both fishes and sharks inherit, and each fish
+may have a different strategy. Same can be said about the sharks.
 
-A major point of the environment is exchangeability --- there is a base animal
-class from which both fishes and sharks inherit, and each fish may have a
-different strategy. Same can be said about the sharks.
-
-\begin{figure}
+\begin{figure}[ht!]
   \includegraphics[width=\linewidth]{demo.png}
@@
 
+Different research projects train different components of the environment. This
+guide will focus on training the shark, however there have been publications
+that trained the fishes~\cite{HPGBL19}. The publication referred to here also
+adapted the action space to only allow each animal to turn their angle. Thus,
+while the action space below will be explained in its complete state, but
+depending on the project some elements could be simplified.
+
+\subsection{Action Space}
+
+The environment expects a `joint\_shark\_action', i.e.\ a dictionary where
+sharks are the keys and the action itself is the value. The action consists of
+three values: speed, angle and whether to procreate.
+
 \subsection{Observation Space}
+
+The observation returned is structured as a dictionary with each shark as the
+key and its respective observation as the value. Now, the observation includes
+a few status informations about the shark itself but also the animals it sees.
+For scalability, only a subset of animals can be observed, making the
+environment a partially observable one. Specifically, the orientation (scaled
+from radians to the range $[-1, 1]$) and the readiness to procreate ar
+eincluded as status information. Next, distance and angle to each wall that is
+in the view distance of the current shark is added. Since there are 4 walls,
+this results in 8 values. If walls are disabled (i.e.\ a torus is used), the 8
+values are replaced by zeroes. One of the main principles of the environment is
+a consistent observation space, which is achieved by this sort of zero-padding.
+Next, $n$ 3-tuple slots are used for sharks that may or may not be visible. $n$
+is a hyperparameter that is set beforehand and stays constant throughout
+training and evaluation. One 3-tuple slot consists of the distance to the other
+shark, the angle to the shark and the orientation of the other shark. Sharks
+that are outside of the visible range lead to zero-padding. After this, $m$
+slots of the same structure are available for the fishes.
+
+\subsection{Reward}
+The environment returns a dictionary with sharks as keys and the reward
+attained by the respective shark. The reward of a shark increases by $+10$ when
+it eats a fish.
+
+% Here step() return: obs, reward
 
@@
 
-\subsection{Action Space}
+\bibliographystyle{alpha}
+\bibliography{bibliography}
 

### 2020-11-15 guide/compile.sh

@@ -1,1 +1,3 @@
 pdflatex guide.tex
+bibtex guide
+pdflatex guide.tex

### 2020-11-17 guide/guide.tex
Add information regarding step() to guide.

@@
 environment a partially observable one. Specifically, the orientation (scaled
-from radians to the range $[-1, 1]$) and the readiness to procreate ar
-eincluded as status information. Next, distance and angle to each wall that is
+from radians to the range $[-1, 1]$) and the readiness to procreate are
+included as status information. Next, distance and angle to each wall that is
 in the view distance of the current shark is added. Since there are 4 walls,
@@
 \subsection{Reward}
+
 The environment returns a dictionary with sharks as keys and the reward
@@
 
-% Here step() return: obs, reward
+\subsection{Step}
 
-% TODO: Partial observability.
+After a step in the environment, the standard 3-tuple known for gym
+environments is returned. However, all three elements of that tuple are
+dictionaries with sharks as keys and the observation, reward and done flag for
+the respective shark as the value.
+
+\subsection{Further Settings}
+
+% TODO: Radius
 

### 2020-11-17 basic_main.py
Small fix in basic_main.

@@ -18,14 +18,15 @@ if __name__ == '__main__':
     )
 
     env.select_fish_types(
-        Random_Fish=0,
-        Turn_Away_Fish=5,
-        Boid_Fish=0
+        random_fish=0,
+        turn_away_fish=5,
+        boid_fish=0
     )
 
     env.select_shark_types(Shark_Agents=1)
 
     for training_episode in range(1, EPISODES + 1):
+        print(training_episode)
         joint_shark_observation = env.reset()
         while not env.is_finished:
             shark_joint_action = {}
@@ -35,5 +36,6 @@ if __name__ == '__main__':
                 )
                 shark_joint_action[shark_name] = action
             new_state = env.step(shark_joint_action)
+            print(new_state[2])
             joint_shark_observation = new_state[0]
             env.render()

### 2020-11-17 env/aquarium.py
Rename fish types.

@@ -138,10 +138,10 @@ class Aquarium:
     def killed_sharks(self) -> int:
         return self.dead_sharks
 
-    def select_fish_types(self, Random_Fish=0, Turn_Away_Fish=0, Boid_Fish=0):
-        self.fish_types['RandomFish'] = Random_Fish
-        self.fish_types['TurnAwayFish'] = Turn_Away_Fish
-        self.fish_types['BoidFish'] = Boid_Fish
+    def select_fish_types(self, random_fish=0, turn_away_fish=0, boid_fish=0):
+        self.fish_types['RandomFish'] = random_fish
+        self.fish_types['TurnAwayFish'] = turn_away_fish
+        self.fish_types['BoidFish'] = boid_fish
         return self
 
     def select_shark_types(self, Shark_Agents=0):

### 2020-11-17 main.py
Add first major PPO test.

@@ -1,14 +1,60 @@
 #!/usr/bin/env python3
+import os
+import time
+import numpy as np
+from gym import spaces
 from baselines import logger
-from baselines.common import tf_util as U
-from baselines.ppo1 import mlp_policy, pposgd_simple
+from baselines import bench
+from baselines.ppo2 import ppo2
 from env.aquarium import Aquarium
+
+
+os.environ['OPENAI_LOGDIR'] = '/tmp'
+os.environ['OPENAI_LOG_FORMAT'] = 'stdout,tensorboard'
+
+
+class EnvWrapper(bench.Monitor):
+    def __init__(self, env):
+        self.env = env
+        self.env.action_space = spaces.Box(low=-1.0, high=1.0, shape=(2,))
+        # spaces.Tuple((
+        #     spaces.Box(low=-1.0, high=1.0, shape=(1,)),
+        #     spaces.Box(low=-1.0, high=1.0, shape=(1,)),
+        #     spaces.Discrete(2)
+        # ))
+        self.n = 2 + self.env.observable_sharks * 3 +\
+            self.env.observable_fishes * 3 +\
+            self.env.observable_walls * 2
+        self.env.observation_space = spaces.Box(
+            low=-1.0, high=1.0, shape=(self.n,)
+        )
+        self.env.reward_range = (-float('inf'), float('inf'))
+        self.env.spec = None
+        self.env.metadata = {'render.modes': ['human']}
+        self.env.num_envs = 1
+        bench.Monitor.__init__(
+            self, self.env, 'log' + str(int(time.time())) + '.txt'
+        )
+
+    def step(self, action):
+        sharks = list(self.env.sharks)
+        if not sharks:
+            # TODO .. yikes
+            return ([0.] * self.n, 0, True, {})
+        shark = sharks[0]
+        action = (action[0][0], action[0][1], False)
+        obs, reward, done = self.env.step({shark.name: action})
+        shark = next(iter(done.keys()))
+        return (obs.get(shark, np.array([0.] * self.n)), reward[shark], done[shark], {})
+
+    def reset(self):
+        obs = self.env.reset()
+        shark = next(iter(obs.keys()))
+        return obs[shark]
 
 
 class Experiment:
     def __init__(self):
-        self.num_timesteps = 10000
-
         self.env = Aquarium(
             nr_sharks=1,
             nr_fishes=10,
@@ -21,37 +67,45 @@ class Experiment:
             max_sharks=1,
             torus=False,
[…]

### 2020-11-19 basic_main.py
Rename variables in select_shark_types.

@@ -23,7 +23,7 @@ if __name__ == '__main__':
         boid_fish=0
     )
 
-    env.select_shark_types(Shark_Agents=1)
+    env.select_shark_types(shark_agents=1)
 
     for training_episode in range(1, EPISODES + 1):
         print(training_episode)

### 2020-11-19 env/aquarium.py

@@ -149,13 +149,13 @@ class Aquarium:
         self.fish_types['BoidFish'] = boid_fish
         return self
 
-    def select_shark_types(self, Shark_Agents=0):
+    def select_shark_types(self, shark_agents=0):
         # TODO: Update the docstring below.
         """Derzeit gibt es not keine Möglichkeit, statische und normale Agent zu kombinieren
            Das kommt noch"""
         #self.shark_types['RandomShark'] = Random_Shark
         #self.shark_types['DefaultShark'] = Default_Shark
-        self.shark_types['Shark_Agents'] = Shark_Agents
+        self.shark_types['shark_agents'] = shark_agents
         return self
 
     def reset(self) -> np.array:
@@ -219,9 +219,9 @@ class Aquarium:
 
         # TODO Make this a global variable.
         types = {
-            "RandomShark": RandomShark,
-            "DefaultShark": DefaultShark,
-            "Shark_Agents": SharkAgent
+            "random_shark": RandomShark,
+            "default_shark": DefaultShark,
+            "shark_agents": SharkAgent
         }
 
         x_pos = np.random.uniform(0, self.width)

### 2020-11-19 config.py
Add config handling (simulations.json) and improve custom logger.

@@ -1,0 +1,19 @@
+import copy
+import json
+
+
+class Config:
+    def __init__(self):
+        with open('simulations.json', 'r') as f:
+            self.cfg = json.load(f)
+
+    def get_cfg(self, cfg_id):
+        base_cfg = self.cfg[self.cfg[cfg_id].get('base_cfg', cfg_id)]
+        cfg = copy.deepcopy(base_cfg)
+        if cfg_id not in self.cfg:
+            raise Exception(
+                'Error: Key %s does not exist in simulations.json.' % cfg_id
+            )
+        cfg.update(self.cfg[cfg_id])
+        cfg['cfg_id'] = cfg_id
+        return cfg

### 2020-11-19 custom_logger.py

@@ -25,12 +25,12 @@ class Logger:
         self.custom_metrics = defaultdict(list)
         self.custom_file = self.logdir + "/custom.pickle"
 
-    def log_summary(self, env, rewards, n_episode):
-        tf.summary.scalar('Train/Tot_Reward', sum(rewards), n_episode)
-        tf.summary.scalar('Train/Dead_Fishes', env.dead_fishes, n_episode)
-        tf.summary.scalar('Train/Dead_Sharks', env.dead_sharks, n_episode)
-        self.log_file('Train/Fish_Population', env.fish_population_counter)
-        self.log_file('Train/Shark_Population', env.shark_population_counter)
+    def log_summary(self, env, rewards, n_episode, prefix='Train'):
+        tf.summary.scalar(prefix + '/Tot_Reward', sum(rewards), n_episode)
+        tf.summary.scalar(prefix + '/Dead_Fishes', env.dead_fishes, n_episode)
+        tf.summary.scalar(prefix + '/Dead_Sharks', env.dead_sharks, n_episode)
+        self.log_file(prefix + '/Fish_Population', env.fish_population_counter)
+        self.log_file(prefix + '/Shark_Population', env.shark_population_counter)
 
     def log_kv(self, k, v, step):
         tf.summary.scalar(k, v, step)

### 2020-11-19 main.py

@@ -1,13 +1,17 @@
 #!/usr/bin/env python3
 import os
-import time
+import sys
+import json
+
 import numpy as np
+from gym.core import Wrapper
 from gym import spaces
-from custom_logger import Logger
 from baselines import logger
-from baselines import bench
 from baselines.ppo2 import ppo2
+
 from env.aquarium import Aquarium
+from custom_logger import Logger
+from config import Config
 
 
 os.environ['OPENAI_LOGDIR'] = 'runs/'
@@ -16,15 +20,10 @@ os.environ['OPENAI_LOGDIR'] = 'runs/'
 os.environ['OPENAI_LOG_FORMAT'] = 'stdout'
 
 
-class EnvWrapper(bench.Monitor):
+class EnvWrapper(Wrapper):
     def __init__(self, env):
         self.env = env
         self.env.action_space = spaces.Box(low=-1.0, high=1.0, shape=(2,))
-        # spaces.Tuple((
-        #     spaces.Box(low=-1.0, high=1.0, shape=(1,)),
-        #     spaces.Box(low=-1.0, high=1.0, shape=(1,)),
-        #     spaces.Discrete(2)
-        # ))
         self.n = 2 + self.env.observable_sharks * 3 +\
             self.env.observable_fishes * 3 +\
             self.env.observable_walls * 2
@@ -35,9 +34,7 @@ class EnvWrapper(bench.Monitor):
         self.env.spec = None
         self.env.metadata = {'render.modes': ['human']}
         self.env.num_envs = 1
-        bench.Monitor.__init__(
-            self, self.env, 'log' + str(int(time.time())) + '.txt'
-        )
+        Wrapper.__init__(self, env=env)
 
     def step(self, action):
         sharks = list(self.env.sharks)
@@ -48,7 +45,12 @@ class EnvWrapper(bench.Monitor):
         action = (action[0][0], action[0][1], False)
         obs, reward, done = self.env.step({shark.name: action})
         shark = next(iter(done.keys()))
-        return (obs.get(shark, np.array([0.] * self.n)), reward[shark], done[shark], {})
+        return (
+            obs.get(shark, np.array([0.] * self.n)),
+            reward[shark],
+            done[shark],
+            {}
+        )
 
     def reset(self):
         obs = self.env.reset()
@@ -57,61 +59,90 @@ class EnvWrapper(bench.Monitor):
 
 
 class Experiment:
-    def __init__(self):
[…]

### 2020-11-19 main.py
Add support for changing the network structure from config.

@@ -102,7 +102,8 @@ class Experiment:
             env=self.env,
             network=self.cfg['ppo']['network'],
             total_timesteps=total_timesteps,
-            seed=self.cfg['ppo']['seed'],
+            # TODO Seed..
+            # seed=self.cfg['ppo']['seed'],
             # TODO: For now for consistency we use Aquarium max_steps as nsteps
             nsteps=max_steps,
             ent_coef=self.cfg['ppo']['ent_coef'],
@@ -116,6 +117,8 @@ class Experiment:
             noptepochs=self.cfg['ppo']['noptepochs'],
             cliprange=self.cfg['ppo']['cliprange'],
             save_interval=self.cfg['ppo']['save_interval'],
+            num_layers=self.cfg['ppo']['num_layers'],
+            num_hidden=self.cfg['ppo']['num_hidden'],
             tb_logger=self.tb_logger,
             evaluator=self.evaluate
         )

### 2020-11-20 config.py
Fix base_cfg handling.

@@ -14,6 +14,10 @@ class Config:
             raise Exception(
                 'Error: Key %s does not exist in simulations.json.' % cfg_id
             )
-        cfg.update(self.cfg[cfg_id])
+        # We support one level for now.
+        for k in self.cfg[cfg_id].keys():
+            if k == 'base_cfg':
+                continue
+            cfg[k].update(self.cfg[cfg_id][k])
         cfg['cfg_id'] = cfg_id
         return cfg

### 2020-11-20 plottex/a.tex
Add plottex.

\documentclass{standalone}
        \usepackage{tikz,pgfplots}

        \pgfplotsset{compat=1.10}

        \usepgfplotslibrary{fillbetween,external}
        \tikzexternalize

        \begin{document}

        \begin{tikzpicture}
            \begin{axis}[
                thick,smooth,no markers,
                grid=both,
                grid style={line width=.1pt, draw=gray!10},
                xlabel={Steps},
                ylabel={Train/Tot_Reward}]
            ]
            \addplot+[name path=A,black,line width=1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};
            \addplot+[name path=B,black,line width=.1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};
            \addplot+[name path=C,black,line width=.1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};
            \addplot+[name path=D,black,line width=.1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};
            \addplot+[name path=E,black,line width=.1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};

            \addplot+[name path=F,black,line width=.1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};
            \addplot+[name path=G,black,line width=.1pt] coordinates {(0, 0.0)(1, 0.0)(2, 0.0)(3, 0.0)(4, 0.0)(5, 0.0)(6, 0.0)(7, 0.0)(8, 0.0)(9, 0.0)(10, 0.0)(11, 0.0)(12, 0.0)(13, 0.0)(14, 0.0)(15, 0.0)(16, 0.0)(17, 0.0)(18, 0.0)(19, 0.0)(20, 0.0)(21, 0.0)(22, 0.0)(23, 0.0)(24, 0.0)(25, 0.0)(26, 0.0)(27, 0.0)(28, 0.0)(29, 0.0)(30, 0.0)(31, 0.0)(32, 0.0)(33, 0.0)(34, 0.0)(35, 0.0)(36, 0.0)(37, 0.0)(38, 0.0)(39, 0.0)(40, 0.0)(41, 0.0)(42, 0.0)(43, 0.0)(44, 0.0)(45, 0.0)(46, 0.0)(47, 0.0)(48, 0.0)(49, 0.0)(50, 0.0)(51, 0.0)(52, 0.0)(53, 0.0)(54, 0.0)(55, 0.0)(56, 0.0)(57, 0.0)(58, 0.0)(59, 0.0)(60, 0.0)(61, 0.0)(62, 0.0)(63, 0.0)(64, 0.0)(65, 0.0)(66, 0.0)(67, 0.0)(68, 0.0)(69, 0.0)(70, 0.0)(71, 0.0)(72, 0.0)(73, 0.0)(74, 0.0)(75, 0.0)(76, 0.0)(77, 0.0)(78, 0.0)(79, 0.0)(80, 0.0)(81, 0.0)(82, 0.0)(83, 0.0)(84, 0.0)(85, 0.0)(86, 0.0)(87, 0.0)(88, 0.0)(89, 0.0)(90, 0.0)(91, 0.0)(92, 0.0)(93, 0.0)(94, 0.0)(95, 0.0)(96, 0.0)(97, 0.0)(98, 0.0)(99, 0.0)(100, 0.0)(101, 0.0)(102, 0.0)(103, 0.0)(104, 0.0)(105, 0.0)(106, 0.0)(107, 0.0)(108, 0.0)(109, 0.0)(110, 0.0)(111, 0.0)(112, 0.0)(113, 0.0)(114, 0.0)(115, 0.0)(116, 0.0)(117, 0.0)(118, 0.0)(119, 0.0)(120, 0.0)(121, 0.0)(122, 0.0)(123, 0.0)(124, 0.0)(125, 0.0)(126, 0.0)(127, 0.0)(128, 0.0)(129, 0.0)(130, 0.0)(131, 0.0)(132, 0.0)(133, 0.0)(134, 0.0)(135, 0.0)(136, 0.0)(137, 0.0)(138, 0.0)(139, 0.0)(140, 0.0)(141, 0.0)(142, 0.0)(143, 0.0)(144, 0.0)(145, 0.0)(146, 0.0)(147, 0.0)(148, 0.0)(149, 0.0)(150, 0.0)(151, 0.0)(152, 0.0)(153, 0.0)(154, 0.0)(155, 0.0)(156, 0.0)(157, 0.0)(158, 0.0)(159, 0.0)(160, 0.0)(161, 0.0)(162, 0.0)(163, 0.0)(164, 0.0)(165, 0.0)(166, 0.0)(167, 0.0)(168, 0.0)(169, 0.0)(170, 0.0)(171, 0.0)(172, 0.0)(173, 0.0)(174, 0.0)(175, 0.0)(176, 0.0)(177, 0.0)(178, 0.0)(179, 0.0)(180, 0.0)(181, 0.0)(182, 0.0)(183, 0.0)(184, 0.0)(185, 0.0)(186, 0.0)(187, 0.0)(188, 0.0)(189, 0.0)(190, 0.0)(191, 0.0)(192, 0.0)(193, 0.0)(194, 0.0)(195, 0.0)(196, 0.0)(197, 0.0)(198, 0.0)(199, 0.0)(200, 0.0)(201, 0.0)(202, 0.0)(203, 0.0)(204, 0.0)(205, 0.0)(206, 0.0)(207, 0.0)(208, 0.0)(209, 0.0)(210, 0.0)(211, 0.0)(212, 0.0)(213, 0.0)(214, 0.0)(215, 0.0)(216, 0.0)(217, 0.0)(218, 0.0)(219, 0.0)(220, 0.0)(221, 0.0)(222, 0.0)(223, 0.0)(224, 0.0)(225, 0.0)(226, 0.0)(227, 0.0)(228, 0.0)(229, 0.0)(230, 0.0)(231, 0.0)(232, 0.0)(233, 0.0)(234, 0.0)(235, 0.0)(236, 0.0)(237, 0.0)(238, 0.0)(239, 0.0)(240, 0.0)(241, 0.0)(242, 0.0)(243, 0.0)(244, 0.0)(245, 0.0)(246, 0.0)(247, 0.0)(248, 0.0)(249, 0.0)(250, 0.0)(251, 0.0)(252, 0.0)(253, 0.0)(254, 0.0)(255, 0.0)(256, 0.0)(257, 0.0)(258, 0.0)(259, 0.0)(260, 0.0)(261, 0.0)(262, 0.0)(263, 0.0)(264, 0.0)(265, 0.0)(266, 0.0)(267, 0.0)(268, 0.0)(269, 0.0)(270, 0.0)(271, 0.0)(272, 0.0)(273, 0.0)(274, 0.0)(275, 0.0)(276, 0.0)(277, 0.0)(278, 0.0)(279, 0.0)(280, 0.0)(281, 0.0)(282, 0.0)(283, 0.0)(284, 0.0)(285, 0.0)(286, 0.0)(287, 0.0)(288, 0.0)(289, 0.0)(290, 0.0)(291, 0.0)(292, 0.0)(293, 0.0)(294, 0.0)(295, 0.0)(296, 0.0)(297, 0.0)(298, 0.0)(299, 0.0)(300, 0.0)(301, 0.0)(302, 0.0)(303, 0.0)(304, 0.0)(305, 0.0)(306, 0.0)(307, 0.0)(308, 0.0)(309, 0.0)(310, 0.0)(311, 0.0)(312, 0.0)(313, 0.0)(314, 0.0)(315, 0.0)(316, 0.0)(317, 0.0)(318, 0.0)(319, 0.0)(320, 0.0)(321, 0.0)(322, 0.0)(323, 0.0)(324, 0.0)(325, 0.0)(326, 0.0)(327, 0.0)(328, 0.0)(329, 0.0)(330, 0.0)(331, 0.0)(332, 0.0)(333, 0.0)(334, 0.0)(335, 0.0)(336, 0.0)(337, 0.0)(338, 0.0)(339, 0.0)(340, 0.0)(341, 0.0)(342, 0.0)(343, 0.0)(344, 0.0)(345, 0.0)(346, 0.0)(347, 0.0)(348, 0.0)(349, 0.0)(350, 0.0)(351, 0.0)(352, 0.0)(353, 0.0)(354, 0.0)(355, 0.0)(356, 0.0)(357, 0.0)(358, 0.0)(359, 0.0)(360, 0.0)(361, 0.0)(362, 0.0)(363, 0.0)(364, 0.0)(365, 0.0)(366, 0.0)(367, 0.0)(368, 0.0)(369, 0.0)(370, 0.0)(371, 0.0)(372, 0.0)(373, 0.0)(374, 0.0)(375, 0.0)(376, 0.0)(377, 0.0)(378, 0.0)(379, 0.0)(380, 0.0)(381, 0.0)(382, 0.0)(383, 0.0)(384, 0.0)(385, 0.0)(386, 0.0)(387, 0.0)(388, 0.0)(389, 0.0)(390, 0.0)(391, 0.0)(392, 0.0)(393, 0.0)(394, 0.0)(395, 0.0)(396, 0.0)(397, 0.0)(398, 0.0)(399, 0.0)(400, 0.0)(401, 0.0)(402, 0.0)(403, 0.0)(404, 0.0)(405, 0.0)(406, 0.0)(407, 0.0)(408, 0.0)(409, 0.0)(410, 0.0)(411, 0.0)(412, 0.0)(413, 0.0)(414, 0.0)(415, 0.0)(416, 0.0)(417, 0.0)(418, 0.0)(419, 0.0)(420, 0.0)(421, 0.0)(422, 0.0)(423, 0.0)(424, 0.0)(425, 0.0)(426, 0.0)(427, 0.0)(428, 0.0)(429, 0.0)(430, 0.0)(431, 0.0)(432, 0.0)(433, 0.0)(434, 0.0)(435, 0.0)(436, 0.0)(437, 0.0)(438, 0.0)(439, 0.0)(440, 0.0)(441, 0.0)(442, 0.0)(443, 0.0)(444, 0.0)(445, 0.0)(446, 0.0)(447, 0.0)(448, 0.0)(449, 0.0)(450, 0.0)(451, 0.0)(452, 0.0)(453, 0.0)(454, 0.0)(455, 0.0)(456, 0.0)(457, 0.0)(458, 0.0)(459, 0.0)(460, 0.0)(461, 0.0)(462, 0.0)(463, 0.0)(464, 0.0)(465, 0.0)(466, 0.0)(467, 0.0)(468, 0.0)(469, 0.0)(470, 0.0)(471, 0.0)(472, 0.0)(473, 0.0)(474, 0.0)(475, 0.0)(476, 0.0)(477, 0.0)(478, 0.0)(479, 0.0)(480, 0.0)(481, 0.0)(482, 0.0)(483, 0.0)(484, 0.0)(485, 0.0)(486, 0.0)(487, 0.0)(488, 0.0)(489, 0.0)(490, 0.0)(491, 0.0)(492, 0.0)(493, 0.0)(494, 0.0)(495, 0.0)(496, 0.0)(497, 0.0)(498, 0.0)(499, 0.0)(500, 0.0)(501, 0.0)(502, 0.0)(503, 0.0)(504, 0.0)(505, 0.0)(506, 0.0)(507, 0.0)(508, 0.0)(509, 0.0)(510, 0.0)(511, 0.0)(512, 0.0)(513, 0.0)(514, 0.0)(515, 0.0)(516, 0.0)(517, 0.0)(518, 0.0)(519, 0.0)(520, 0.0)(521, 0.0)(522, 0.0)(523, 0.0)(524, 0.0)(525, 0.0)(526, 0.0)(527, 0.0)(528, 0.0)(529, 0.0)(530, 0.0)(531, 0.0)(532, 0.0)(533, 0.0)(534, 0.0)(535, 0.0)(536, 0.0)(537, 0.0)(538, 0.0)(539, 0.0)(540, 0.0)(541, 0.0)(542, 0.0)(543, 0.0)(544, 0.0)(545, 0.0)(546, 0.0)(547, 0.0)(548, 0.0)(549, 0.0)(550, 0.0)(551, 0.0)(552, 0.0)(553, 0.0)(554, 0.0)(555, 0.0)(556, 0.0)(557, 0.0)(558, 0.0)(559, 0.0)(560, 0.0)(561, 0.0)(562, 0.0)(563, 0.0)(564, 0.0)(565, 0.0)(566, 0.0)(567, 0.0)(568, 0.0)(569, 0.0)(570, 0.0)(571, 0.0)(572, 0.0)(573, 0.0)(574, 0.0)(575, 0.0)(576, 0.0)(577, 0.0)(578, 0.0)(579, 0.0)(580, 0.0)(581, 0.0)(582, 0.0)(583, 0.0)(584, 0.0)(585, 0.0)(586, 0.0)(587, 0.0)(588, 0.0)(589, 0.0)(590, 0.0)(591, 0.0)(592, 0.0)(593, 0.0)(594, 0.0)(595, 0.0)(596, 0.0)(597, 0.0)(598, 0.0)(599, 0.0)(600, 0.0)(601, 0.0)(602, 0.0)(603, 0.0)(604, 0.0)(605, 0.0)(606, 0.0)(607, 0.0)(608, 0.0)(609, 0.0)(610, 0.0)(611, 0.0)(612, 0.0)(613, 0.0)(614, 0.0)(615, 0.0)(616, 0.0)(617, 0.0)(618, 0.0)(619, 0.0)(620, 0.0)(621, 0.0)(622, 0.0)(623, 0.0)(624, 0.0)(625, 0.0)(626, 0.0)(627, 0.0)(628, 0.0)(629, 0.0)(630, 0.0)(631, 0.0)(632, 0.0)(633, 0.0)(634, 0.0)(635, 0.0)(636, 0.0)(637, 0.0)(638, 0.0)(639, 0.0)(640, 0.0)(641, 0.0)(642, 0.0)(643, 0.0)(644, 0.0)(645, 0.0)(646, 0.0)(647, 0.0)(648, 0.0)(649, 0.0)(650, 0.0)(651, 0.0)(652, 0.0)(653, 0.0)(654, 0.0)(655, 0.0)(656, 0.0)(657, 0.0)(658, 0.0)(659, 0.0)(660, 0.0)(661, 0.0)(662, 0.0)(663, 0.0)(664, 0.0)(665, 0.0)(666, 0.0)(667, 0.0)(668, 0.0)(669, 0.0)(670, 0.0)(671, 0.0)(672, 0.0)(673, 0.0)(674, 0.0)(675, 0.0)(676, 0.0)(677, 0.0)(678, 0.0)(679, 0.0)(680, 0.0)(681, 0.0)(682, 0.0)(683, 0.0)(684, 0.0)(685, 0.0)(686, 0.0)(687, 0.0)(688, 0.0)(689, 0.0)(690, 0.0)(691, 0.0)(692, 0.0)(693, 0.0)(694, 0.0)(695, 0.0)(696, 0.0)(697, 0.0)(698, 0.0)(699, 0.0)(700, 0.0)(701, 0.0)(702, 0.0)(703, 0.0)(704, 0.0)(705, 0.0)(706, 0.0)(707, 0.0)(708, 0.0)(709, 0.0)(710, 0.0)(711, 0.0)(712, 0.0)(713, 0.0)(714, 0.0)(715, 0.0)(716, 0.0)(717, 0.0)(718, 0.0)(719, 0.0)(720, 0.0)(721, 0.0)(722, 0.0)(723, 0.0)(724, 0.0)(725, 0.0)(726, 0.0)(727, 0.0)(728, 0.0)(729, 0.0)(730, 0.0)(731, 0.0)(732, 0.0)(733, 0.0)(734, 0.0)(735, 0.0)(736, 0.0)(737, 0.0)(738, 0.0)(739, 0.0)(740, 0.0)(741, 0.0)(742, 0.0)(743, 0.0)(744, 0.0)(745, 0.0)(746, 0.0)(747, 0.0)(748, 0.0)(749, 0.0)(750, 0.0)(751, 0.0)(752, 0.0)(753, 0.0)(754, 0.0)(755, 0.0)(756, 0.0)(757, 0.0)(758, 0.0)(759, 0.0)(760, 0.0)(761, 0.0)(762, 0.0)(763, 0.0)(764, 0.0)(765, 0.0)(766, 0.0)(767, 0.0)(768, 0.0)(769, 0.0)(770, 0.0)(771, 0.0)(772, 0.0)(773, 0.0)(774, 0.0)(775, 0.0)(776, 0.0)(777, 0.0)(778, 0.0)(779, 0.0)(780, 0.0)(781, 0.0)(782, 0.0)(783, 0.0)(784, 0.0)(785, 0.0)(786, 0.0)(787, 0.0)(788, 0.0)(789, 0.0)(790, 0.0)(791, 0.0)(792, 0.0)(793, 0.0)(794, 0.0)(795, 0.0)(796, 0.0)(797, 0.0)(798, 0.0)(799, 0.0)(800, 0.0)(801, 0.0)(802, 0.0)(803, 0.0)(804, 0.0)(805, 0.0)(806, 0.0)(807, 0.0)(808, 0.0)(809, 0.0)(810, 0.0)(811, 0.0)(812, 0.0)(813, 0.0)(814, 0.0)(815, 0.0)(816, 0.0)(817, 0.0)(818, 0.0)(819, 0.0)(820, 0.0)(821, 0.0)(822, 0.0)(823, 0.0)(824, 0.0)(825, 0.0)(826, 0.0)(827, 0.0)(828, 0.0)(829, 0.0)(830, 0.0)(831, 0.0)(832, 0.0)(833, 0.0)(834, 0.0)(835, 0.0)(836, 0.0)(837, 0.0)(838, 0.0)(839, 0.0)(840, 0.0)(841, 0.0)(842, 0.0)(843, 0.0)(844, 0.0)(845, 0.0)(846, 0.0)(847, 0.0)(848, 0.0)(849, 0.0)(850, 0.0)(851, 0.0)(852, 0.0)(853, 0.0)(854, 0.0)(855, 0.0)(856, 0.0)(857, 0.0)(858, 0.0)(859, 0.0)(860, 0.0)(861, 0.0)(862, 0.0)(863, 0.0)(864, 0.0)(865, 0.0)(866, 0.0)(867, 0.0)(868, 0.0)(869, 0.0)(870, 0.0)(871, 0.0)(872, 0.0)(873, 0.0)(874, 0.0)(875, 0.0)(876, 0.0)(877, 0.0)(878, 0.0)(879, 0.0)(880, 0.0)(881, 0.0)(882, 0.0)(883, 0.0)(884, 0.0)(885, 0.0)(886, 0.0)(887, 0.0)(888, 0.0)(889, 0.0)(890, 0.0)(891, 0.0)(892, 0.0)(893, 0.0)(894, 0.0)(895, 0.0)(896, 0.0)(897, 0.0)(898, 0.0)(899, 0.0)(900, 0.0)(901, 0.0)(902, 0.0)(903, 0.0)(904, 0.0)(905, 0.0)(906, 0.0)(907, 0.0)(908, 0.0)(909, 0.0)(910, 0.0)(911, 0.0)(912, 0.0)(913, 0.0)(914, 0.0)(915, 0.0)(916, 0.0)(917, 0.0)(918, 0.0)(919, 0.0)(920, 0.0)(921, 0.0)(922, 0.0)(923, 0.0)(924, 0.0)(925, 0.0)(926, 0.0)(927, 0.0)(928, 0.0)(929, 0.0)(930, 0.0)(931, 0.0)(932, 0.0)(933, 0.0)(934, 0.0)(935, 0.0)(936, 0.0)(937, 0.0)(938, 0.0)(939, 0.0)(940, 0.0)(941, 0.0)(942, 0.0)(943, 0.0)(944, 0.0)(945, 0.0)(946, 0.0)(947, 0.0)(948, 0.0)(949, 0.0)(950, 0.0)(951, 0.0)(952, 0.0)(953, 0.0)(954, 0.0)(955, 0.0)(956, 0.0)(957, 0.0)(958, 0.0)(959, 0.0)(960, 0.0)(961, 0.0)(962, 0.0)(963, 0.0)(964, 0.0)(965, 0.0)(966, 0.0)(967, 0.0)(968, 0.0)(969, 0.0)(970, 0.0)(971, 0.0)(972, 0.0)(973, 0.0)(974, 0.0)(975, 0.0)(976, 0.0)(977, 0.0)(978, 0.0)(979, 0.0)(980, 0.0)(981, 0.0)(982, 0.0)(983, 0.0)(984, 0.0)(985, 0.0)(986, 0.0)(987, 0.0)(988, 0.0)(989, 0.0)(990, 0.0)(991, 0.0)(992, 0.0)(993, 0.0)(994, 0.0)(995, 0.0)(996, 0.0)(997, 0.0)(998, 0.0)(999, 0.0)(1000, 0.0)(1001, 0.0)(1002, 0.0)(1003, 0.0)(1004, 0.0)(1005, 0.0)(1006, 0.0)(1007, 0.0)(1008, 0.0)(1009, 0.0)(1010, 0.0)(1011, 0.0)(1012, 0.0)(1013, 0.0)(1014, 0.0)(1015, 0.0)(1016, 0.0)(1017, 0.0)(1018, 0.0)(1019, 0.0)(1020, 0.0)(1021, 0.0)(1022, 0.0)(1023, 0.0)(1024, 0.0)(1025, 0.0)(1026, 0.0)(1027, 0.0)(1028, 0.0)(1029, 0.0)(1030, 0.0)(1031, 0.0)(1032, 0.0)(1033, 0.0)(1034, 0.0)(1035, 0.0)(1036, 0.0)(1037, 0.0)(1038, 0.0)(1039, 0.0)(1040, 0.0)(1041, 0.0)(1042, 0.0)(1043, 0.0)(1044, 0.0)(1045, 0.0)(1046, 0.0)(1047, 0.0)(1048, 0.0)(1049, 0.0)(1050, 0.0)(1051, 0.0)(1052, 0.0)(1053, 0.0)(1054, 0.0)(1055, 0.0)(1056, 0.0)(1057, 0.0)(1058, 0.0)(1059, 0.0)(1060, 0.0)(1061, 0.0)(1062, 0.0)(1063, 0.0)(1064, 0.0)(1065, 0.0)(1066, 0.0)(1067, 0.0)(1068, 0.0)(1069, 0.0)(1070, 0.0)(1071, 0.0)(1072, 0.0)(1073, 0.0)(1074, 0.0)(1075, 0.0)(1076, 0.0)(1077, 0.0)(1078, 0.0)(1079, 0.0)(1080, 0.0)(1081, 0.0)(1082, 0.0)(1083, 0.0)(1084, 0.0)(1085, 0.0)(1086, 0.0)(1087, 0.0)(1088, 0.0)(1089, 0.0)(1090, 0.0)(1091, 0.0)(1092, 0.0)(1093, 0.0)(1094, 0.0)(1095, 0.0)(1096, 0.0)(1097, 0.0)(1098, 0.0)(1099, 0.0)(1100, 0.0)(1101, 0.0)(1102, 0.0)(1103, 0.0)(1104, 0.0)(1105, 0.0)(1106, 0.0)(1107, 0.0)(1108, 0.0)(1109, 0.0)(1110, 0.0)(1111, 0.0)(1112, 0.0)(1113, 0.0)(1114, 0.0)(1115, 0.0)(1116, 0.0)(1117, 0.0)(1118, 0.0)(1119, 0.0)(1120, 0.0)(1121, 0.0)(1122, 0.0)(1123, 0.0)(1124, 0.0)(1125, 0.0)(1126, 0.0)(1127, 0.0)(1128, 0.0)(1129, 0.0)(1130, 0.0)(1131, 0.0)(1132, 0.0)(1133, 0.0)(1134, 0.0)(1135, 0.0)(1136, 0.0)(1137, 0.0)(1138, 0.0)(1139, 0.0)(1140, 0.0)(1141, 0.0)(1142, 0.0)(1143, 0.0)(1144, 0.0)(1145, 0.0)(1146, 0.0)(1147, 0.0)(1148, 0.0)(1149, 0.0)(1150, 0.0)(1151, 0.0)(1152, 0.0)(1153, 0.0)(1154, 0.0)(1155, 0.0)(1156, 0.0)(1157, 0.0)(1158, 0.0)(1159, 0.0)(1160, 0.0)(1161, 0.0)(1162, 0.0)(1163, 0.0)(1164, 0.0)(1165, 0.0)(1166, 0.0)(1167, 0.0)(1168, 0.0)(1169, 0.0)(1170, 0.0)(1171, 0.0)(1172, 0.0)(1173, 0.0)(1174, 0.0)(1175, 0.0)(1176, 0.0)(1177, 0.0)(1178, 0.0)(1179, 0.0)(1180, 0.0)(1181, 0.0)(1182, 0.0)(1183, 0.0)(1184, 0.0)(1185, 0.0)(1186, 0.0)(1187, 0.0)(1188, 0.0)(1189, 0.0)(1190, 0.0)(1191, 0.0)(1192, 0.0)(1193, 0.0)(1194, 0.0)(1195, 0.0)(1196, 0.0)(1197, 0.0)(1198, 0.0)(1199, 0.0)(1200, 0.0)(1201, 0.0)(1202, 0.0)(1203, 0.0)(1204, 0.0)(1205, 0.0)(1206, 0.0)(1207, 0.0)(1208, 0.0)(1209, 0.0)(1210, 0.0)(1211, 0.0)(1212, 0.0)(1213, 0.0)(1214, 0.0)(1215, 0.0)(1216, 0.0)(1217, 0.0)(1218, 0.0)(1219, 0.0)(1220, 0.0)(1221, 0.0)(1222, 0.0)(1223, 0.0)(1224, 0.0)(1225, 0.0)(1226, 0.0)(1227, 0.0)(1228, 0.0)(1229, 0.0)(1230, 0.0)(1231, 0.0)(1232, 0.0)(1233, 0.0)(1234, 0.0)(1235, 0.0)(1236, 0.0)(1237, 0.0)(1238, 0.0)(1239, 0.0)(1240, 0.0)(1241, 0.0)(1242, 0.0)(1243, 0.0)(1244, 0.0)(1245, 0.0)(1246, 0.0)(1247, 0.0)(1248, 0.0)(1249, 0.0)(1250, 0.0)(1251, 0.0)(1252, 0.0)(1253, 0.0)(1254, 0.0)(1255, 0.0)(1256, 0.0)(1257, 0.0)(1258, 0.0)(1259, 0.0)(1260, 0.0)(1261, 0.0)(1262, 0.0)(1263, 0.0)(1264, 0.0)(1265, 0.0)(1266, 0.0)(1267, 0.0)(1268, 0.0)(1269, 0.0)(1270, 0.0)(1271, 0.0)(1272, 0.0)(1273, 0.0)(1274, 0.0)(1275, 0.0)(1276, 0.0)(1277, 0.0)(1278, 0.0)(1279, 0.0)(1280, 0.0)(1281, 0.0)(1282, 0.0)(1283, 0.0)(1284, 0.0)(1285, 0.0)(1286, 0.0)(1287, 0.0)(1288, 0.0)(1289, 0.0)(1290, 0.0)(1291, 0.0)(1292, 0.0)(1293, 0.0)(1294, 0.0)(1295, 0.0)(1296, 0.0)(1297, 0.0)(1298, 0.0)(1299, 0.0)(1300, 0.0)(1301, 0.0)(1302, 0.0)(1303, 0.0)(1304, 0.0)(1305, 0.0)(1306, 0.0)(1307, 0.0)(1308, 0.0)(1309, 0.0)(1310, 0.0)(1311, 0.0)(1312, 0.0)(1313, 0.0)(1314, 0.0)(1315, 0.0)(1316, 0.0)(1317, 0.0)(1318, 0.0)(1319, 0.0)(1320, 0.0)(1321, 0.0)(1322, 0.0)(1323, 0.0)(1324, 0.0)(1325, 0.0)(1326, 0.0)(1327, 0.0)(1328, 0.0)(1329, 0.0)(1330, 0.0)(1331, 0.0)(1332, 0.0)(1333, 0.0)(1334, 0.0)(1335, 0.0)(1336, 0.0)(1337, 0.0)(1338, 0.0)(1339, 0.0)(1340, 0.0)(1341, 0.0)(1342, 0.0)(1343, 0.0)(1344, 0.0)(1345, 0.0)(1346, 0.0)(1347, 0.0)(1348, 0.0)(1349, 0.0)(1350, 0.0)(1351, 0.0)(1352, 0.0)(1353, 0.0)(1354, 0.0)(1355, 0.0)(1356, 0.0)(1357, 0.0)(1358, 0.0)(1359, 0.0)(1360, 0.0)(1361, 0.0)(1362, 0.0)(1363, 0.0)(1364, 0.0)(1365, 0.0)(1366, 0.0)(1367, 0.0)(1368, 0.0)(1369, 0.0)(1370, 0.0)(1371, 0.0)(1372, 0.0)(1373, 0.0)(1374, 0.0)(1375, 0.0)(1376, 0.0)(1377, 0.0)(1378, 0.0)(1379, 0.0)(1380, 0.0)(1381, 0.0)(1382, 0.0)(1383, 0.0)(1384, 0.0)(1385, 0.0)(1386, 0.0)(1387, 0.0)(1388, 0.0)(1389, 0.0)(1390, 0.0)(1391, 0.0)(1392, 0.0)(1393, 0.0)(1394, 0.0)(1395, 0.0)(1396, 0.0)(1397, 0.0)(1398, 0.0)(1399, 0.0)(1400, 0.0)(1401, 0.0)(1402, 0.0)(1403, 0.0)(1404, 0.0)(1405, 0.0)(1406, 0.0)(1407, 0.0)(1408, 0.0)(1409, 0.0)(1410, 0.0)(1411, 0.0)(1412, 0.0)(1413, 0.0)(1414, 0.0)(1415, 0.0)(1416, 0.0)(1417, 0.0)(1418, 0.0)(1419, 0.0)(1420, 0.0)(1421, 0.0)(1422, 0.0)(1423, 0.0)(1424, 0.0)(1425, 0.0)(1426, 0.0)(1427, 0.0)(1428, 0.0)(1429, 0.0)(1430, 0.0)(1431, 0.0)(1432, 0.0)(1433, 0.0)(1434, 0.0)(1435, 0.0)(1436, 0.0)(1437, 0.0)(1438, 0.0)(1439, 0.0)(1440, 0.0)(1441, 0.0)(1442, 0.0)(1443, 0.0)(1444, 0.0)(1445, 0.0)(1446, 0.0)(1447, 0.0)(1448, 0.0)(1449, 0.0)(1450, 0.0)(1451, 0.0)(1452, 0.0)(1453, 0.0)(1454, 0.0)(1455, 0.0)(1456, 0.0)(1457, 0.0)(1458, 0.0)(1459, 0.0)(1460, 0.0)(1461, 0.0)(1462, 0.0)(1463, 0.0)(1464, 0.0)(1465, 0.0)(1466, 0.0)(1467, 0.0)(1468, 0.0)(1469, 0.0)(1470, 0.0)(1471, 0.0)(1472, 0.0)(1473, 0.0)(1474, 0.0)(1475, 0.0)(1476, 0.0)(1477, 0.0)(1478, 0.0)(1479, 0.0)(1480, 0.0)(1481, 0.0)(1482, 0.0)(1483, 0.0)(1484, 0.0)(1485, 0.0)(1486, 0.0)(1487, 0.0)(1488, 0.0)(1489, 0.0)(1490, 0.0)(1491, 0.0)(1492, 0.0)(1493, 0.0)(1494, 0.0)(1495, 0.0)(1496, 0.0)(1497, 0.0)(1498, 0.0)(1499, 0.0)(1500, 0.0)(1501, 0.0)(1502, 0.0)(1503, 0.0)(1504, 0.0)(1505, 0.0)(1506, 0.0)(1507, 0.0)(1508, 0.0)(1509, 0.0)(1510, 0.0)(1511, 0.0)(1512, 0.0)(1513, 0.0)(1514, 0.0)(1515, 0.0)(1516, 0.0)(1517, 0.0)(1518, 0.0)(1519, 0.0)};

            \addplot+[name path=ZZZ,red,line width=.3pt] coordinates {};

            \addplot[blue!50,fill opacity=0.2] fill between[of=A and B];
            \addplot[blue!50,fill opacity=0.2] fill between[of=A and C];
            \addplot[blue!50,fill opacity=0.2] fill between[of=A and D];
            \addplot[blue!50,fill opacity=0.2] fill between[of=A and E];
            \end{axis}
        \end{tikzpicture}
        \end{document}

### 2020-11-20 gen_plot.py

@@ -1,0 +1,228 @@
+import glob
+import sys
+import os
+from collections import defaultdict
+
+import numpy as np
+
+from tensorflow.core.util import event_pb2
+from tensorflow.python.lib.io import tf_record
+
+
+def my_summary_iterator(path):
+    for r in tf_record.tf_record_iterator(path):
+        yield event_pb2.Event.FromString(r)
+
+
+def smooth(y, box_pts):
+    box = np.ones(box_pts) / box_pts
+    y_smooth = np.convolve(y, box, mode='same')
+    return y_smooth
+
+
+def aggregate(path):
+    keys = [
+        'Train/Tot_Reward',
+        # 'Eval/Length',
+        # 'Eval/MCTS_Confidence',
+        # 'Train/AvgLoss'
+        # 'Eval/MCTS_Confidence'
+    ]
+
+    agg_runs = defaultdict(lambda: defaultdict(list))
+    agg_keys = {}
+
+    path = glob.glob(os.path.join(path, "events.out.tfevents.*"))[0]
+    for event in my_summary_iterator(path):
+        if not event.summary.value:
+            continue
+        tag = event.summary.value[0].tag
+        for key in keys:
+            if tag.startswith(key):
+                run = tag[tag.rfind('/')+1:]
+                agg_runs[key][run].append(event.summary.value[0].simple_value)
+
+    for key in agg_runs:
+        aggregated = []
+        for run in agg_runs[key]:
+            aggregated.append(agg_runs[key][run])
+        max_len = max(len(x) for x in aggregated)
+        aggregated_ = []
+        for i, x in enumerate(aggregated):
+            aggregated_.append(
+                np.pad(
+                    x,
+                    (0, max_len - len(x)),
+                    mode='constant',
+                    constant_values=(0, x[-1])
+                )
+            )
+        agg_keys[key] = np.array(aggregated_)
+
+    return agg_runs, agg_keys
+
+
+def gen_tex_single_key(data, key, use_percentile):
+    print(data[:, -1])
+    if use_percentile:
+        new_data = [
+            # Smoothing loses 20 data points.
+            # smooth(np.percentile(data, percentile, axis=0), 20)[10:-9]
+            smooth(np.percentile(data, percentile, axis=0), 2)[1:-1]
+            for percentile in [50, 10, 25, 75, 90, 0, 100]
+        ]
+    else:
+        stddev = np.var(data, axis=0, ddof=1) ** .5
+        mean = np.average(data, axis=0)
[…]

### 2020-11-20 main.py
Refactor evaluation function in main a bit and add param config 4.

@@ -120,13 +120,14 @@ class Experiment:
             num_layers=self.cfg['ppo']['num_layers'],
             num_hidden=self.cfg['ppo']['num_hidden'],
             tb_logger=self.tb_logger,
-            evaluator=self.evaluate
+            evaluator=self.evaluate_and_log
         )
 
         # import pdb; pdb.set_trace()  # noqa
-        self.evaluate(model, int(total_timesteps / max_steps))
+        self.evaluate_and_log(model, int(total_timesteps / max_steps))
 
     def evaluate(self, model, n_episode):
+        """Run an evaluation game."""
         obs = self.env.reset()
         i = 0
         rewards = []
@@ -143,9 +144,19 @@ class Experiment:
             if done:
                 break
         print(tot_rew)
+        return rewards
+
+    def evaluate_and_log(self, model, n_episode):
+        """Run an evaluation game and log to tensorboard."""
+        rewards = self.evaluate(model, n_episode)
         self.tb_logger.log_summary(self.env, rewards, n_episode, prefix='Eval')
 
 
 if __name__ == '__main__':
     cfg_id = sys.argv[1]
-    Experiment(cfg_id).train()
+    if len(sys.argv) > 2:
+        from shark_baselines import get_model
+        experiment = Experiment(cfg_id)
+        print('TOT REW', sum(experiment.evaluate(get_model(experiment.env), 0)))
+    else:
+        Experiment(cfg_id).train()

### 2020-11-20 shark_baselines.py
Add deterministic shark baseline.

@@ -1,0 +1,13 @@
+import tensorflow as tf
+from env.animal_controller import DefaultSharkController
+
+
+def get_model(env):
+    class Model:
+        def step(obs):
+            obs = env.prepare_observation_for_controller(obs[0])
+            action = DefaultSharkController.get_action(**obs)
+            return tf.convert_to_tensor(
+                [[[action[0], action[1]]]]
+            )
+    return Model

### 2020-11-20 custom_logger.py
Also log current config to tensorboard.

@@ -12,18 +12,19 @@ lock = threading.Lock()
 
 
 class Logger:
-    def __init__(self, cfg_id):
+    def __init__(self, cfg):
         _id = "-".join([
             datetime.datetime.now().strftime("%y-%m-%d_%H:%M:%S"),
             str(int(random.random() * 1000)),
             socket.gethostname(),
-            cfg_id
+            cfg['cfg_id']
         ])
         self.logdir = "runs/" + _id
         self.writer = tf.summary.create_file_writer(self.logdir)
         self.writer.set_as_default()
         self.custom_metrics = defaultdict(list)
         self.custom_file = self.logdir + "/custom.pickle"
+        tf.summary.text('Info/Params', str(cfg))
 
     def log_summary(self, env, rewards, n_episode, prefix='Train'):
         tf.summary.scalar(prefix + '/Tot_Reward', sum(rewards), n_episode)

### 2020-11-20 main.py

@@ -92,7 +92,7 @@ class Experiment:
         self.env = EnvWrapper(self.env)
 
     def train(self):
-        self.tb_logger = Logger(self.cfg['cfg_id'])
+        self.tb_logger = Logger(self.cfg)
         logger.configure()
 
         total_timesteps = self.cfg['ppo']['total_timesteps']

### 2020-12-14 env/aquarium.py
Add evaluator and visualize script. Also add the herding check.

@@ -396,6 +396,16 @@ class Aquarium:
                     if fish in self.fishes:
                         self.fishes.remove(fish)
                     if shark in self.track_shark_reward:
+                        # This was to check whether we have real cooperation or
+                        # herding.
+                        # Well, we have herding.
+                        #
+                        # for shark_ in self.sharks:
+                        #     if shark_ == shark:
+                        #         print('s', shark_.starving_indicator())
+                        #     else:
+                        #         print('o', shark_.starving_indicator())
+                        # print('')
                         self.track_shark_reward[shark] += 10
                         self.shark_tot_reward[shark] += 10
                         self.dead_fishes += 1

### 2020-12-14 env/shark.py

@@ -60,6 +60,10 @@ class Shark(Animal, ABC):
         max_survival_time = self.INITIAL_SURVIVAL_TIME + self.eaten_fish * self.PROLONGED_SURVIVAL_PER_EATEN_FISH
         return (self.survived_n_steps / max_survival_time) >= 1
 
+    def starving_indicator(self):
+        max_survival_time = self.INITIAL_SURVIVAL_TIME + self.eaten_fish * self.PROLONGED_SURVIVAL_PER_EATEN_FISH
+        return self.survived_n_steps / max_survival_time
+
     # Override
     def name(self):
         return 'Shark.' + str(self._identifier)

### 2020-12-14 evaluator.py

@@ -1,0 +1,149 @@
+import sys
+import glob
+import pickle
+import multiprocessing
+from multiprocessing import Process
+from collections import OrderedDict
+
+
+def load(id_, cfg_id, return_dict):
+    base_cfg_id = 'ma3_obs'
+    res = list(glob.glob("models/%s-*-F" % cfg_id))
+    # print(res)
+    counter_coop = 0.
+    counter_fail = 0.
+    counter_greedy = 0.
+    for fname in res:
+        print('#############################')
+        print(fname)
+        from main import Experiment
+        for _ in range(3):
+            fish_pop_hist = Experiment(base_cfg_id, show_gui=False).load_eval(fname, steps=5000)
+            if fish_pop_hist[-1] > 0 and fish_pop_hist[-1] < 10:
+                counter_coop += 1
+            if fish_pop_hist[-1] == 0:
+                counter_greedy += 1
+            if fish_pop_hist[-1] >= 10:
+                counter_fail += 1
+
+        total = counter_coop + counter_greedy + counter_fail
+        print('c:%d' %counter_coop, 'f:%d' % counter_fail, 'g:%d' % counter_greedy, 't:%d' % total)
+
+    print('coop', counter_coop / total)
+    print('greedy', counter_greedy / total)
+    print('fail', counter_fail / total)
+    return_dict[id_] = (counter_coop / total, total)
+    # return id_, (counter_coop / total, total)
+
+
+def main(id_):
+    multiprocessing.set_start_method('spawn')
+
+    cfg_ids_i10_p75 = {
+        't200': 'ma3_obs_starve_maxsteps_t200',
+        't300': 'ma3_obs_starve_maxsteps_t300',
+        't400': 'ma3_obs_starve_maxsteps_t400',
+        't500': 'ma3_obs_starve_maxsteps_t500',
+        't600': 'ma3_obs_starve_maxsteps_t600',
+        't700': 'ma3_obs_starve_maxsteps_t700',
+        't800': 'ma3_obs_starve_maxsteps_t800',
+        't1000': 'ma3_obs_starve_maxsteps',
+        't1200': 'ma3_obs_starve_maxsteps_t1200',
+        't1500': 'ma3_obs_starve_maxsteps_t1500',
[…]

### 2020-12-14 main.py

@@ -456,13 +456,14 @@ class Experiment:
         self.env.model = model
         return model
 
-    def load_eval(self, model_filename):
+    def load_eval(self, model_filename, steps=10000):
         if self.two_nets:
             return self._load_eval_two_nets(model_filename)
         self.show_gui = True
-        self.env.env.max_steps = 10000
+        self.env.env.max_steps = steps
         model = self.load(model_filename)
         self.evaluate(model, 0)
+        return self.env.fish_population_counter
 
     def _load_eval_two_nets(self, model_filename):
         self.show_gui = True
@@ -594,5 +595,5 @@ if __name__ == '__main__':
         # Just do 3 runs. I can cancel whenever I want.
         # Use multi_scancel.sh to cancel multiple jobs in a range.
         print('DEPRECATED! USE SINGLE OR MULTI KEYWORD!')
-        for _ in range(3):
+        for _ in range(2):
             Experiment(cfg_id).train()

### 2020-12-14 visualize.py

@@ -1,0 +1,55 @@
+import pickle
+import matplotlib.pyplot as plt
+
+
+print('ATTENTION! YOURE USING THE DEC 14 PICKLES!')
+print('ATTENTION! YOURE USING THE DEC 14 PICKLES!')
+print('ATTENTION! YOURE USING THE DEC 14 PICKLES!')
+
+#base_path = 'pickles_14Dec/'
+base_path = ''
+
+with open(base_path + 'i10_p150.pickle', 'rb') as f:
+    i10_p150 = pickle.load(f)
+with open(base_path + 'i10_p75.pickle', 'rb') as f:
+    i10_p75 = pickle.load(f)
+with open(base_path + 'i5_p150.pickle', 'rb') as f:
+    i5_p150 = pickle.load(f)
+with open(base_path + 'i5_p75.pickle', 'rb') as f:
+    i5_p75 = pickle.load(f)
+
+
+print(i10_p150)
+print(i10_p75)
+print(i5_p150)
+print(i5_p75)
+
+
+# All in one scatter plot.
+# plt.scatter(i10_p150[0], [x[0] for x in i10_p150[1]], c='g')
+# plt.scatter(i10_p75[0], [x[0] for x in i10_p75[1]], c='r')
+# plt.scatter(i5_p75[0], [x[0] for x in i5_p75[1]], c='b')
+# plt.scatter(i5_p150[0], [x[0] for x in i5_p150[1]], c='c')
+# plt.show()
+
+# Two plots.
+fig, axs = plt.subplots(1, 2, figsize=(11, 5), sharey=True)
+axs[0].set_title('10 initial fishes')
+axs[0].set_ylabel('Herding/Coop rate')
+axs[0].set_xlabel('Initial shark survival time t')
+axs[0].scatter([x[1:] for x in i10_p150[0]], [x[0] for x in i10_p150[1]], c='g', label='p150')
+axs[0].scatter([x[1:] for x in i10_p75[0]], [x[0] for x in i10_p75[1]], c='r', label='p75')
+axs[0].legend()
+axs[1].set_title('5 initial fishes')
+axs[1].set_ylabel('Herding/Coop rate')
+axs[1].set_xlabel('Initial shark survival time t')
+axs[1].scatter([x[1:] for x in i5_p150[0]], [x[0] for x in i5_p150[1]], c='g', label='p150')
[…]

### 2020-12-15 paper/paper.tex
Add correct official ALIFE template.

\documentclass[letterpaper]{article}

\usepackage{natbib,alifeconf}  %% The order is important

% *****************
%  Requirements:
% *****************
%
% - All pages sized consistently at 8.5 x 11 inches (US letter size).
% - PDF length <= 8 pages for full papers, <=2 pages for extended
%    abstracts (not including citations).
% - Abstract length <= 250 words.
% - No visible crop marks.
% - Images at no greater than 300 dpi, scaled at 100%.
% - Embedded open type fonts only.
% - All layers flattened.
% - No attachments.
% - All desired links active in the files.

% Note that the PDF file must not exceed 5 MB if it is to be indexed
% by Google Scholar. Additional information about Google Scholar
% can be found here:
% http://www.google.com/intl/en/scholar/inclusion.html.

% If your system does not generate letter format documents by default,
% you can use the following workflow:
% latex example
% bibtex example
% latex example ; latex example
% dvips -o example.ps -t letterSize example.dvi
% ps2pdf example.ps example.pdf

% For pdflatex users:
% The alifeconf style file loads the "graphicx" package, and
% this may lead some users of pdflatex to experience problems.
% These can be fixed by editing the alifeconf.sty file to specify:
% \usepackage[pdftex]{graphicx}
%   instead of
% \usepackage{graphicx}.
% The PDF output generated by pdflatex should match the required
% specifications and obviously the dvips and ps2pdf steps become
% unnecessary.

% Note:  Some laser printers have a serious problem printing TeX
% output. The use of ps type I fonts should avoid this problem.

\title{Critical Exponent of Species-Size Distribution in Evolution}
\author{Chris Adami$^{1}$, Ryoichi Seki$^{1,2}$ \and Robel Yirdaw$^2$ \\
\mbox{}\\
$^1$California Institute of Technology, Pasadena, CA 91125 \\
$^2$California State University, Northridge, CA 91330 \\
adami@caltech.edu} % email of corresponding author

% For several authors from the same institution use the same number to
% refer to one address.
%
% If the names do not fit well on one line use
%         Author 1, Author 2 ... \\ {\Large\bf Author n} ...\\ ...
%
% If the title and author information do not fit in the area
% allocated, place \setlength\titlebox{<new height>} after the
% \documentclass line where <new height> is 2.25in

\begin{document}
\maketitle

\begin{abstract}
% Abstract length should not exceed 250 words
  We analyze the geometry of the species-- and genotype-size
  distribution in evolving and adapting populations of single-stranded
  self-replicating genomes: here programs in the Avida world.  We find
  that a scale-free distribution (power law) emerges in complex
  landscapes that achieve a separation of two fundamental time scales:
  the relaxation time (time for population to return to equilibrium
  after a perturbation) and the time between mutations that produce
  fitter genotypes. The latter can be dialed by changing the mutation
  rate.  In the scaling regime, we determine the
  critical exponent of the distribution of sizes and strengths of
  avalanches in a system without coevolution, described by first-order
  phase transitions in single finite niches.
\end{abstract}

\section{Introduction}

Power law distributions in Nature usually signal the absence of a
scale in the region where the scaling is observed, and sometimes point
to critical dynamics. In Self-Organized-Criticality (SOC)
\citep{BTW87,BTW88}, for example, power law distributions reveal the
dynamics of an unstable critical point, brought about by slow driving
and a feed-back mechanism between order parameter and critical
parameter.  The critical dynamics is usually described within the
language of second-order phase transitions in condensed matter systems
\citep{SJD}, but it can be shown that SOC-type behavior also occurs
within a dual description in terms of the Landau-Ginzburg equation as
{\em first-order} transitions \citep{GS}.  Indeed, it was shown that a
power law distribution of {\em epoch-lengths}, that is, the time a
particular species dominates the dynamics of an adapting population,
is explained by a self-organized critical scenario \citep{CA2} that
carries the hallmark of first-order phase transitions. Here, we
measure the distribution of abundances of {\em species} and genotypes
in an artificial chemistry, \citep[the Avida Artificial Life
system][]{AB1,OBA} and show that the distribution is scale-free under
a broad class of circumstances, confirming the results reported in
\citep{CA2}.  In the next section, we discuss the first-order dynamics
in more detail and examine ``avalanches of invention'' from the point
of view of a thermodynamics of information. In Section III, we measure
the critical exponent of the power law of genotype abundances in the
limit of infinitesimal driving, i.e., infinitesimal mutation rate, and
discuss the role of the fitness landscape in shaping the
distribution. In Section IV, we repeat the analysis for a higher
taxonomic level (that of species) and discuss its relation to the
geometric distributions found by \citet{BUR90,BUR93}.
Conclusions about the evolutionary process drawn from the data
obtained in this paper are presented in Section V.

\section{Self-Organization in Evolution}

The idea that the evolutionary process occurs in spurts, jumps, and
bursts rather than gradual, slow and continuous changes has been
around for over 75 years \citep{WIL}, but has gained prominence as
``punctuated equilibrium'' through the work of \citet{GE77,GE93}. The
general idea is that evolutionary innovations are not bestowed upon an
existing species as a whole, gradually, but rather by the emergence of
{\em one} better adapted mutant which, by its superiority, serves as
the seed of a new breed that sweeps through an ecological niche and
supplants the species previously occupying it. The global dynamics
thus has a microscopic origin, as shown experimentally, e.g., in
populations of {\it E. Coli} \citep{ECL96}.

Such avalanches can be viewed in two apparently contradictory ways. On
the one hand we may consider the wave of extinction touching all
species that are connected by their ecological relations, a process
akin to percolation and therefore suitably described by the language
of second-order critical phenomena \citep{BS}. Such a scenario relies
on the {\em coevolution} of species (to build their ecological
relations) and successfully describes power-law distributions obtained
from the fossil record \citep{SB96,BP96}. There is, on the other hand,
a description in terms of {\em informational} avalanches that does not
require coevolution and leads to the same statistics, as we show
here. Rather than contradicting the aforementioned picture
\citep{NFST}, we believe it to be complementary.

In the following, we set up a scenario in which {\em information} is
viewed as the agent of self-organization in evolving and adapting
populations. Information is, in the strict sense of Shannon theory, a
measure of correlation between two ensembles: here a population of
genomes and the environment it is adapting to. As described elsewhere
\citep{IAL}, this correlation grows as the population stores more and
more information about the environment via random measurements,
implementing a very effective {\em natural Maxwell demon}. Any time a
stochastic event increases the information stored in the population, a
wave of extinction removes the less adapted genomes and establishes a
new era. Yet, information cannot leave the population as a whole,
which therefore may be thought of as protected by a {\em
semi-permeable membrane} for information, the hallmark of the Maxwell
demon. Let us consider this dynamics in more detail.

The simple living systems we consider here are populations of
self-replicating strings of instructions, coded in an alphabet of
dimension ${\cal D}$ with variable string length $\ell$. The total
number of possible strings is exponentially large. Here, we consider
the subset of all strings currently in existence in a finite
population of size $N$, harboring $N_g$ different types, where
$N_g\ll{\cal D}^\ell$. Each {\em genotype} (particular sequence of
instructions) is characterized by its replication rate $\epsilon_i$,
which depends on the sequence only, while its survival rate is given
by $\epsilon_i/\langle \epsilon\rangle$, in a ``stirred-reactor''
environment that allows a mean-field picture. This average replication
rate $\langle \epsilon\rangle$ characterizes the fitness of the
population as a whole, and is given by
\begin{eqnarray}
\langle \epsilon\rangle=\sum_i^{N_g}\frac{n_i}N \epsilon_i\;,
\end{eqnarray}
where $n_i$ is the {\em occupation number}, or frequency, of genotype
$i$ in the population. As $N_g$ is not fixed in time, the average
depends on time also, and is to be taken over all genotypes currently
living. The total abundance, or size, of a genotype is then
\begin{eqnarray}
s_i=\int_0^\infty n_i(t)\, dt=\int_{T_c}^{T_e}n_i(t)\, dt\;,
\label{size}
\end{eqnarray}
where $T_c$ is the time of creation of this particular genotype, and
$T_e$ the moment of extinction. Before we obtain this distribution in
Avida, let us delve further into the statistical description of the
extinction events.

At any point in time, the fate of every string in the population is
determined by the craftiness of the best adapted member of the
population, described by $\epsilon_{\rm best}$. In this simple,
finite, world, which does not permit strings to affect other members
of the population except by replacing them, not being the best reduces
a string to an ephemeral existence. Thus, every string is
characterized by a {\em relative} fitness, or {\em inferiority}
\begin{eqnarray}
E_i=\epsilon_{\rm best}-\epsilon_i
\end{eqnarray}
which plays the role of an {\em energy} variable for strings of
information {IAL}. Naturally, $\langle E\rangle=0$ characterizes the
{\em ground state}, or vacuum, of the population, and strings with
$E_i>0$ can be viewed as occupying {\em excited} states, soon to
``decay'' to the ground state (by being replaced by a string with
vanishing inferiority). Through such processes, the dynamics of the
system tend to minimize the average inferiority of the population, and
the fitness landscape of replication rates thus provides a Lyapunov
function. Consequently, we are allowed to proceed with our statistical
analysis. Imagine a population in equilibrium, at minimal average
inferiority as allowed by the ``temperature'': the rate (or more
precisely, the probability) of mutation. Imagine further that a
mutation event produces a new genotype, fitter than the others,
exploiting the environment in novel ways, replicating faster than all
the others. It is thus endowed with a new best replication rate,
$\epsilon_{\rm best}^{\rm new}$, larger than the old ``best'' by an
amount $\Delta \epsilon$, and redefining what it means to be
inferior. Indeed, all inferiorities must now be {\em renormalized}:
what passed as a ground state ($E=0$) string before now suddenly finds
itself in an excited state. The seed of a new generation has been
sown, a phase transition must occur. In the picture just described,
this is a first-order phase transition with latent heat
$\Delta\epsilon$ (see Fig.\ref{fig1}), starting at the ``nucleation''
point, and leading to an expanding {\em bubble} of ``new phase''.

\begin{figure}[t]
\begin{center}
\includegraphics[width=2.1in,angle=-90]{fig1.eps}
\caption{``Energies'' (inferiorities) of strings in a first-order
  phase transition with latent heat $\Delta\epsilon$.}
\label{fig1}
\end{center}
\end{figure}

This bubble expands with a speed given by the Fisher velocity
\begin{eqnarray}
v\sim\sqrt{D\Delta\epsilon}\;, \label{eq4}
\end{eqnarray}
where $D$ is the diffusion coefficient (of information) in this
medium, until the entire population has been converted \citep{CHU}.
This marks the end of the phase transition, as the population returns
to equilibrium via mutations acting on the new species, creating new
diversity and restoring the {\em entropy} of the population to its
previous value. This prepares the stage for a new avalanche, as only
an equilibrated population is vulnerable to even the smallest
perturbation. The system has returned to a critical point, driven by
mutations, self-organized by information.

Thus we see how a first-order scenario, without coevolution, can lead
to self-organized and critical dynamics. It takes place within a
single, finite, ecological niche, and thus does not contradict the
dynamics taking place for populations that span many niches. Rather,
we must conclude that the descriptions complement each other, from the
single-niche level to the ecological web. Let us now take a closer
look at the statistics of avalanches in this model, i.e., at the
distribution of genotype sizes.

\section{Exponents and Power Laws}

\hyphenation{ap-proximated}

In this particular system avalanche size can be approximated
by the size $s$ of the genotype that gave rise to it,
Eq.~(\ref{size}).  We shall measure the distribution of these sizes
$P(s)$ in the Artificial Life system Avida, which implements a
population of self-replicating computer programs written in a simple
machine language-like instruction set of ${\cal D}=24$ instructions,
with programs of varying sequence length. In the course of
self-replication, these programs produce mutant off-spring because the
{\tt copy} instruction they use is flawed at a rate $R$ errors per
instruction copied, and adapt to an environment in which the
performance of {\em logical} computations on externally provided
numbers is akin to the catalysis of chemical reactions \citep{OBA}. In
this {\em artificial chemistry} therefore, successful computations
accelerate the metabolism (i.e., the CPU) of those strings that carry
the {\em gene} (code) necessary to perform the trick, and any program
discovering a new trick is the seed of another avalanche.

Avida is not a stirred-reactor environment (although one can be
simulated). Rather, the programs live on a two-dimensional grid, each
program occupying one site. The size of the grid is finite, and chosen
in these experiments to be small enough that avalanches are generally
over before a new one starts. As is well-known, this is the condition
{\em sine qua non} for the observation of SOC behavior, a separation
of time scales which implies that the system is driven at
infinitesimal rates.

Let $\tau$ denote the average duration of an avalanche. Then, a
separation of time scales occurs if the average time between the
production of new seeds of avalanches is much larger than $\tau$. New
seeds, in turn, are produced with a frequency $\langle\epsilon\rangle
P$, where $\langle\epsilon\rangle$ is again the average replication
rate, and $P$ is the mutation probability (per replication period) for
an average sequence of length $\ell$,
\begin{eqnarray}
P=1-(1-R)^\ell\;.
\end{eqnarray}
For small enough $R$ and not too large $\ell$ (so that the product
$R\ell$ is smaller than unity) we can approximate
$P\approx R\ell$, and infinitesimal driving occurs in the limit
\begin{eqnarray}
\langle \epsilon\rangle R\ell \ll\frac1\tau\;.\label{cond}
\end{eqnarray}
Furthermore
\begin{eqnarray}
\tau\sim\frac{L}v
\end{eqnarray}
with $L$ the diameter of the system and $v$ a typical Fisher velocity.
The fastest waves are those for which the latent heat is of the order
of the new fitness, i.e., $\Delta\epsilon\sim\epsilon$, in which case
$v\approx \epsilon$ \citep[because $D\sim\epsilon$ in
Eq.~(\ref{eq4}),][]{CHU}, and a separation of time scales is assured
whenever
\begin{eqnarray}
\frac1{R\ell}\gg {L}\;,
\end{eqnarray}
that is, in the limit of vanishing mutation rate or small population
sizes. For the $L=60$ system used here, this condition is obeyed (for
the fastest waves) only for the smallest mutation rate tested and
sequence lengths of the order of the ancestor.

\begin{figure}[t]
\includegraphics[width=2.3in, angle=90]{fig2.eps}
\caption{Fitness of the dominant genotype in the population, $\epsilon_{\rm best}$ as a function of time (in updates).}
\label{fig2}
\end{figure}

In the following, we keep the population size constant (a $60\times60$
grid) and vary the mutation rate. From the previous arguments, we
expect true scale-free dynamics only to appear in the limit of small
mutation rates.  As in this limit avalanches occur less and less
frequently, this is also the limit where data are increasingly
difficult to obtain, and other finite size effects can come into play.
We shall try to isolate the scale-free regime by fitting the
distribution to a power law
\begin{eqnarray}
P(s)\sim s^{-D(R)}\label{power}
\end{eqnarray}
and monitor the behavior of $D$ from low to high mutation rates.

In Fig.~\ref{fig2}, we display a typical history of $\epsilon_{\rm
best}$, i.e., the fitness of the dominant genotype.\footnote{As the
replication rate $\epsilon$ is exponential in the bonus obtained for a
successful computation, $\epsilon_{\rm best}$ increases exponentially
with time.}  Note the ``staircase'' structure of the curve reflecting
the ``punctuated'' dynamics, where each step reflects a new avalanche
and concurrently an extinction event. Staircases very much like these
are also observed in adapting populations of {\it E. Coli}
\citep{LT94}.

As touched upon earlier, the Avida world represents an environment
replete with information, which we encode by providing bonuses for
performing logical computations on externally provided (random)
numbers. The computations rewarded usually involve two inputs $A$ and
$B$, are finite in number and listed in Table~1. At the end of a
typical run (such as Fig.~\ref{fig2}) the population of programs is
usually proficient in almost all tasks for which bonuses are given
out, and the genome length has grown to several multiples of the
initial size to accommodate the acquired information.

\begin{table}[h]
\center{
\begin{tabular}{|c|c|c|c|}\hline
Name & Result & Bonus $b_i$ & Difficulty\\ \hline\hline
Echo & I/O   & 1 & --\\
Not  & $\neg A$ & 2 & 1 \\
Nand & $\neg(A\wedge B)$ & 2 & 1 \\
Not Or & $\neg A \vee B$ & 3 & 2 \\
And  &  $ A \wedge B $   & 3 & 2 \\
Or   &  $ A \vee B $     & 4 & 3 \\
And Not & $A\wedge\neg B$& 4 & 3 \\
Nor  & $\neg(A\vee B)$   & 5 & 4 \\
Xor  & $ A\ {\rm xor}\ B$ &   6 & 4 \\
Equals &$\neg(A\ {\rm xor}\ B)$&6& 4 \\ \hline
\end{tabular}
}
\vskip 0.25cm
\caption{Logical calculations on random inputs $A$ and $B$ rewarded,
bonuses, and difficulty (in minimum number of {\tt nand} instructions
required). Bonuses $b_i$ increase the speed of a CPU by a factor
$\nu_i=1+2^{b_i-3}$.}
\end{table}

Because the amount of information stored in the landscape is finite,
adaptation, and the associated avalanches, must stop when the
population has exhausted the landscape.  However, we shall see that
even a `flat' landscape (on which evolution is essentially neutral
after the sequence has optimized its replicative strategy) gives rise
to a power law of genotype sizes, as long as the programs do not
harbor an excessive amount of ``junk'' instructions.  A typical
abundance distribution (for the run depicted in Fig.~\ref{fig2}) is
shown in Fig.~\ref{fig3}.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=2.25in, angle=90]{fig3.eps}
\caption{Distribution of genotypes sizes $P(s)$ fitted to a power law
  (solid line) at mutation rate $R=0.004$.}
\label{fig3}
\end{center}
\end{figure}

As mentioned earlier, we can also turn {\em off} all bonuses listed in
Tab.~1, in which case fitness is related to replicative abilities
only. Still, avalanches occur (within the first 50,000 updates
monitored) due to minute improvements in fitness, but the length of
the genomes typically stays in the range of the ancestor, a program of
length 31 instructions. We expect a change of dynamics once the
``true'' maximum of the local fitness landscape is reached, however,
we did not reach this regime in the experiments presented here. The
distribution of genotype sizes for the flat landscape is depicted in
Fig.~\ref{fig4}.

\begin{figure}[!tbp]
\begin{center}
\includegraphics[width=2.25in, angle=90]{fig4.eps}
\caption{Distribution of genotypes sizes $P(s)$ for a landscape devoid
  of the bonuses listed in Tab.~1, at mutation rate $R=0.003$.} \label{fig4}
\end{center}
\end{figure}

Clearly then, even such landscapes (flat with respect to all other
activities except replication) are not neutral. Indeed, it is known
that neutral evolution, where the chance for a genotype to increase or
decrease in number is even, leads to a power law in the abundance
distribution with exponent $D=1.5$ \citep{ABH}.

\begin{figure}[t]
\begin{center}
\includegraphics[width=2.2in, angle=90]{fig5.eps}
\vskip 0.25cm
\caption{Fitted exponent of power law for 34 runs at mutation rates
  between $R=0.0005$ and $R=0.01$ copy errors per instruction
  copied. The error bars reflect the standard deviation across the
  sample of runs taken at each mutation rate. The solid line is to
  guide the eye only.
}
\label{fig5}
\end{center}
\end{figure}

In order to test the dependence of the fitted exponent $D(R)$
[Eq.~(\ref{power})] on the mutation rate, we conduct a set of
experiments at varying copy-mutation rates from $0.5\times10^{-3}$ to
$10\times10^{-3}$ and take data for 50,000 updates. Again, a ``best''
genotype is not reached after this time, and we must assume that
avalanches were still occurring at the end of these runs. Furthermore,
in some runs we find that a genotype comes to dominate the population
(usually after most `genes' have been discovered) which carries an
unusual amount of junk instructions. As mentioned earlier, such
species produce a distribution that is exponentially suppressed at
large genotype sizes (data not shown). To avoid contamination from
such species, we stop recording genotypes after a plateau of fitness
was reached, i.e., if the population had discovered most of the
bonuses. Furthermore, in order to minimize finite size effects on the
determination of the critical exponent, we excluded from this fit all
genotype abundances larger than 15, i.e., we only fitted the smallest
abundances. Indeed, at larger mutation rates the higher abundances are
contaminated by a pile-up effect due to the toroidal geometry, while
at lower mutation rates a scale appears to enter which prevents
scale-free behavior. We have not, as yet, been able to determine the
origin of this scale.

In the results reported here, we show the dependence of the fitted
exponent $D$ as a function of the mutation rate $R$ used in the run,
which, however, is a good measure of the mutation probability $P$ only
at small $R$ and if the sequence length is not excessive. As a
consequence, data points at large $R$, as well as runs where an
excessive sequence length developed, carry a systematic error.

\section{Acknowledgements}

This work was supported by NSF grant No.\ PHY-9723972.

\footnotesize
\bibliographystyle{apalike}
\bibliography{paper} % replace by the name of your .bib file

\end{document}

### 2020-12-15 env/aquarium.py
Add kill zone with shared rewards based on distance.

@@ -26,19 +26,21 @@ ACTION_MAX = 1.0
 class Aquarium:
     def __init__(
         self,
-        size: int = 40,
-        observable_sharks: int = 2,
-        observable_fishes: int = 3,
-        observable_walls: int = 2,
-        max_steps: int = 500,
-        max_fish: int = 30,
-        max_sharks: int = 5,
-        water_friction: float = 0.08,
-        torus: bool = False,
-        fish_collision: bool = True,
-        lock_screen: bool = False,
+        size=40,
+        observable_sharks=2,
+        observable_fishes=3,
+        observable_walls=2,
+        max_steps=500,
+        max_fish=30,
+        max_sharks=5,
+        water_friction=0.08,
+        torus=False,
+        fish_collision=True,
+        lock_screen=False,
         seed=42,
-        show_gui=False
+        show_gui=False,
+        shared_kill_zone=False,
+        kill_zone_radius=10.
     ):
         # if seed is None or seed == 'none':
         #     seed = int(1000000000 * np.random.random())
@@ -119,6 +121,10 @@ class Aquarium:
         # k: (shark1, shark2), v: dist
         self.shark_to_shark_dist = defaultdict(list)
         self.shark_to_shark_dist_at_kill = defaultdict(list)
+
+        # Kill zone
+        self.shared_kill_zone = shared_kill_zone
+        self.kill_zone_radius = kill_zone_radius
 
         # GUI
         self.show_gui = show_gui
@@ -342,6 +348,60 @@ class Aquarium:
                 if self.collision_space.check_collision(a1, a2):
                     self.collision_space.perform_collision(a1, a2)
 
+    def _on_shark_fish_collision(self, shark, fish):
+        if fish in self.fishes:
+            self.fishes.remove(fish)
+        if shark in self.track_shark_reward:
+            # This was to check whether we have real cooperation or
+            # herding.
+            # Well, we have herding.
+            #
+            # for shark_ in self.sharks:
+            #     if shark_ == shark:
+            #         print('s', shark_.starving_indicator())
+            #     else:
+            #         print('o', shark_.starving_indicator())
+            # print('')
+
+            if self.shared_kill_zone:
+                for shark_ in self.sharks:
+                    if shark_ == shark:
+                        continue
+                    observation = self.observe_animal(shark_, fish)
+                    dist = observation[0]
+
+                    # TODO This is hacky.
+                    min_dist = shark_.radius + fish.radius
[…]

### 2020-12-15 main.py

@@ -294,7 +294,9 @@ class Experiment:
             fish_collision=self.cfg["aquarium"]["fish_collision"],
             lock_screen=self.cfg["aquarium"]["lock_screen"],
             seed=self.cfg["aquarium"]["seed"],
-            show_gui=self.show_gui
+            show_gui=self.show_gui,
+            shared_kill_zone=self.cfg["aquarium"]["shared_kill_zone"],
+            kill_zone_radius=self.cfg["aquarium"]["kill_zone_radius"]
         )
         self.env.select_fish_types(
             self.cfg["aquarium"]["random_fish"],

### 2020-12-15 env/aquarium.py
Add two new options to sanity check cooperation.

@@ -40,7 +40,9 @@ class Aquarium:
         seed=42,
         show_gui=False,
         shared_kill_zone=False,
-        kill_zone_radius=10.
+        kill_zone_radius=10.,
+        use_global_reward=False,
+        stop_globally_on_first_shark_death=False
     ):
         # if seed is None or seed == 'none':
         #     seed = int(1000000000 * np.random.random())
@@ -66,6 +68,8 @@ class Aquarium:
             self.height
         )
         self.water_friction = water_friction
+        self.use_global_reward = use_global_reward
+        self.stop_globally_on_first_shark_death = stop_globally_on_first_shark_death
 
         # Observation and action space.
         self.observable_walls: int = observable_walls
@@ -399,6 +403,14 @@ class Aquarium:
             else:
                 self.track_shark_reward[shark] += 10
                 self.shark_tot_reward[shark] += 10
+
+                if self.use_global_reward:
+                    for shark_ in self.sharks:
+                        if shark_ == shark:
+                            continue
+                        self.track_shark_reward[shark_] += 10
+                        self.shark_tot_reward[shark_] += 10
+
             self.dead_fishes += 1
             shark.eaten_fish += 1
 
@@ -463,6 +475,9 @@ class Aquarium:
             for a1, a2 in combinations:
                 if self.collision_space.check_collision(a1, a2):
                     self.collision_space.perform_collision(a1, a2)
+
+        if self.stop_globally_on_first_shark_death and len(starved_sharks) > 0:
+            self.sharks = set()
 
     def create_named_shark_observation(self) -> np.array:
         """Creates a dict map the name of each shark to his corresponding

### 2020-12-15 main.py

@@ -296,7 +296,9 @@ class Experiment:
             seed=self.cfg["aquarium"]["seed"],
             show_gui=self.show_gui,
             shared_kill_zone=self.cfg["aquarium"]["shared_kill_zone"],
-            kill_zone_radius=self.cfg["aquarium"]["kill_zone_radius"]
+            kill_zone_radius=self.cfg["aquarium"]["kill_zone_radius"],
+            use_global_reward=self.cfg["aquarium"]["use_global_reward"],
+            stop_globally_on_first_shark_death=self.cfg["aquarium"]["stop_globally_on_first_shark_death"]
         )
         self.env.select_fish_types(
             self.cfg["aquarium"]["random_fish"],

### 2020-12-15 custom_logger.py
Add coop_kills KPI.

@@ -44,6 +44,7 @@ class Logger:
             tf.summary.scalar(prefix + '/Dead_Sharks', env.dead_sharks, n_episode)
             tf.summary.scalar(prefix + '/Last_Fish_Population', fish_pop[-1], n_episode)
             tf.summary.scalar(prefix + '/Last_Shark_Population', shark_pop[-1], n_episode)
+            tf.summary.scalar(prefix + '/Coop_Kills', env.coop_kills, n_episode)
             tf.summary.histogram(prefix + '/Last_Fish_Population_H', fish_pop, n_episode)
             tf.summary.histogram(prefix + '/Last_Shark_Population_H', shark_pop, n_episode)
             tf.summary.histogram(prefix + '/Shark_Speed_H', env.shark_speed_history, n_episode)

### 2020-12-15 env/aquarium.py

@@ -125,6 +125,7 @@ class Aquarium:
         # k: (shark1, shark2), v: dist
         self.shark_to_shark_dist = defaultdict(list)
         self.shark_to_shark_dist_at_kill = defaultdict(list)
+        self.coop_kills = 0
 
         # Kill zone
         self.shared_kill_zone = shared_kill_zone
@@ -191,6 +192,7 @@ class Aquarium:
         self.shark_tot_reward = defaultdict(int)
         self.shark_to_shark_dist = defaultdict(list)
         self.shark_to_shark_dist_at_kill = defaultdict(list)
+        self.coop_kills = 0
 
         # Initialize fishes at random positions.
         for f_type, amount in self.fish_types.items():
@@ -386,6 +388,8 @@ class Aquarium:
                     # They now have to share the reward based on the distance of
                     # the other shark.
                     # TODO: Support multiple sharks at some point.
+
+                    self.coop_kills += 1
 
                     ratio = 1. - dist / radius_dist
                     print(ratio)

### 2020-12-26 custom_logger.pyx
Add full coop ratio KPI.

@@ -48,9 +48,12 @@ class Logger:
             tf.summary.scalar(prefix + '/Coop_Kills', env.coop_kills, n_episode)
             if env.dead_fishes > 0:
                 coop_kills_ratio = env.coop_kills / env.dead_fishes
+                full_coop_kills_ratio = env.full_coop_kills / env.dead_fishes
             else:
                 coop_kills_ratio = 0
+                full_coop_kills_ratio = 0
             tf.summary.scalar(prefix + '/Coop_Kills_Ratio', coop_kills_ratio, n_episode)
+            tf.summary.scalar(prefix + '/Full_Coop_Kills_Ratio', full_coop_kills_ratio, n_episode)
             tf.summary.scalar(prefix + '/Stuns', env.n_stuns, n_episode)
             tf.summary.histogram(prefix + '/Last_Fish_Population_H', fish_pop, n_episode)
             tf.summary.histogram(prefix + '/Last_Shark_Population_H', shark_pop, n_episode)

### 2020-12-26 env/aquarium.pyx

@@ -140,6 +140,7 @@ class Aquarium:
         self.shark_to_shark_dist = defaultdict(list)
         self.shark_to_shark_dist_at_kill = defaultdict(list)
         self.coop_kills = 0
+        self.full_coop_kills = 0
         self.n_stuns = 0
 
         # Kill zone
@@ -209,6 +210,7 @@ class Aquarium:
         self.shark_to_shark_dist = defaultdict(list)
         self.shark_to_shark_dist_at_kill = defaultdict(list)
         self.coop_kills = 0
+        self.full_coop_kills = 0
         self.n_stuns = 0
 
         # Initialize fishes at random positions.
@@ -410,6 +412,8 @@ class Aquarium:
                 n_participating_sharks = len(participating_sharks)
                 if n_participating_sharks > 0:
                     self.coop_kills += 1
+                if n_participating_sharks == len(self.sharks):
+                    self.full_coop_kills += 1
 
                 reward_main_shark = 10. 
                 for shark_, dist, radius_dist in participating_sharks:
@@ -447,7 +451,7 @@ class Aquarium:
 
             self.dead_fishes += 1
             shark.eaten_fish += 1
-            print('coop ratio', self.coop_kills / self.dead_fishes)
+            print('coop ratio', self.coop_kills / self.dead_fishes, 'full coop ratio', self.full_coop_kills / self.dead_fishes)
 
     def _handle_stun_move(self, a1, a2):
         """Make a shark unable to move for a certain number of steps and turn it

### 2020-12-26 gen_plot.py
Add s025 and s02 param configs for net3.

@@ -23,7 +23,8 @@ def smooth(y, box_pts):
 
 def aggregate(path):
     keys = [
-        'Train/Tot_Reward',
+        # 'Train/Tot_Reward',
+        'Train/Last_Fish_Population',
         # 'Eval/Length',
         # 'Eval/MCTS_Confidence',
         # 'Train/AvgLoss'
@@ -64,6 +65,12 @@ def aggregate(path):
             )
         agg_keys[key] = np.array(aggregated_)
 
+    # Lol. Used it for the fish population chart for the paper.
+    # import pickle
+    # a = [float(x) for x in agg_runs['Train/Last_Fish_Population']['Last_Fish_Population']]
+    # with open('a.pickle', 'wb+') as f:
+    #     pickle.dump(a, f)
+    # import pdb; pdb.set_trace()
     return agg_runs, agg_keys
 
 

### 2020-12-27 plots/coop_film_chart/p2.py
Add source files for all current plots.

@@ -1,0 +1,13 @@
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator, FormatStrFormatter
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib._png import read_png
+from matplotlib.cbook import get_sample_data
+
+
+fn = get_sample_data("/Users/instance/Desktop/fword/ritz/fishDomain/plots/coop_film_chart/placeholder3.png", asfileobj=True)
+arr = read_png(fn)
+plt.imshow(arr)
+plt.show()

### 2020-12-27 plots/coop_film_chart/plot.py

@@ -1,0 +1,68 @@
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator, FormatStrFormatter
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib._png import read_png
+from matplotlib.cbook import get_sample_data
+
+
+fig = plt.figure(figsize=(15,5))
+ax = fig.gca(projection='3d', proj_type='ortho')
+
+# ax.set_zlim(-2.01, 1.01)
+# ax.zaxis.set_major_locator(LinearLocator(10))
+# ax.zaxis.set_major_formatter(FormatStrFormatter('%.02f'))
+
+def plot(fname, z, quality=5):
+    fn = get_sample_data("/Users/instance/Desktop/fword/ritz/fishDomain/plots/coop_film_chart/ff/aa/" + fname, asfileobj=True)
+    arr = read_png(fn)
+    # 10 is equal length of x and y axises of your surface
+    stepX, stepY = 10. / arr.shape[0], 10. / arr.shape[1]
+
+    X1 = np.arange(-5, 5, stepX)
+    Y1 = np.arange(-5, 5, stepY)
+    X1, Y1 = np.meshgrid(X1, Y1)
+    # stride args allows to determine image quality 
+    # stride = 1 work slow
+    Z = np.ones(shape=Y1.shape) * z
+    # arr = arr.reshape(100,96,4)
+    print(X1.shape, Y1.shape, arr.shape, Z.shape)
+    ax.plot_surface(X1, Z, Y1, rstride=quality, cstride=quality, facecolors=arr)
+
+
+"""Scaling is done from here.."""
+x_scale=1
+y_scale=2
+z_scale=1
+scale=np.diag([x_scale, y_scale, z_scale, 1.0])
+scale=scale*(1.0 / scale.max())
+scale[3, 3] = 1.0
+def short_proj():
+  return np.dot(Axes3D.get_proj(ax), scale)
+ax.get_proj=short_proj
+"""to here"""
+
+
+ax.view_init(elev=15., azim=-12)
+
+quality = 1
+plot('1.png', 0., quality)
+plot('2.png', 20., quality)
+plot('4.png', 40., quality)
+plot('5.png', 60., quality)
+plot('6.png', 80., quality)
+plot('7.png', 100., quality)
+plot('8.png', 120., quality)
+plot('9.png', 140., quality)
[…]

### 2020-12-27 plots/gen_inn_last_fish_pop_chart.py

@@ -1,0 +1,24 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pickle
+
+
+with open('inn_last_fish_pop.pickle', 'rb') as f:
+    a = pickle.load(f)
+
+
+def moving_average(x, w):
+    return np.convolve(x, np.ones(w), 'valid') / w
+
+
+a = moving_average(a, 100)
+plt.plot(a, linewidth=.8)
+plt.ylabel('Fish population')
+plt.xlabel('Steps in million')
+plt.xticks([0, 1000, 2000, 3000, 4000, 5000, 6000], ['0', '2', '4', '6', '8', '10', '12'])
+plt.axvspan(0, 600, facecolor='#990000', alpha=0.2)
+plt.axvspan(600, 5100, facecolor='#009900', alpha=0.2)
+plt.axvspan(5100, 5900, facecolor='#000099', alpha=0.2)
+# plt.title('a)                                 b)                                   c)')
+plt.title('a                                   b                                    c ')
+plt.show()

### 2020-12-27 plots/shark_speed_chart/gen_vector_plot.py

@@ -1,0 +1,162 @@
+import glob
+import sys
+import os
+from collections import defaultdict
+
+import numpy as np
+
+from tensorflow.core.util import event_pb2
+from tensorflow.python.lib.io import tf_record
+
+from tensorboard.plugins.distribution.compressor import compress_histogram_proto
+
+
+def my_summary_iterator(path):
+    for r in tf_record.tf_record_iterator(path):
+        yield event_pb2.Event.FromString(r)
+
+
+def smooth(y, box_pts):
+    box = np.ones(box_pts) / box_pts
+    y_smooth = np.convolve(y, box, mode='same')
+    return y_smooth
+
+
+def aggregate(path, run_wanted=0):
+    keys = [
+        #'Eval/Reward',
+        # 'Eval/Length',
+        # 'Eval/MCTS_Confidence',
+        #'Train/AvgLoss'
+        # 'Actor/Sample_length',
+        # 'Train/Samples'
+        'Train/Shark_Speed_H'
+    ]
+
+    agg_keys = {
+        k: [] for k in keys
+    }
+
+    path = glob.glob(os.path.join(path, "events.out.tfevents.*"))
+    if not path:
+        return None, None
+    path = path[0]
+
+    import tensorflow as tf
+    i = 0
+    j = 0
+    str_ = ''
+    for event in my_summary_iterator(path):
+        val = event.summary.value
+        if not val:
+            continue
+        tag = event.summary.value[0].tag
+        for key in keys:
+            if tag.startswith(key):
+                # run = tag[tag.rfind('/')+1:]
+                # if int(run) != run_wanted:
+                #     continue
+                x = compress_histogram_proto(event.summary.value[0].histo)
+                # import pdb; pdb.set_trace()
+                agg_keys[key].append([y.value for y in x])
+                if i in [1, 744, 988, 2288, 2971]:
+                    arr = tf.make_ndarray(event.summary.value[0].tensor)
+                    X = (arr[:, 0] + arr[:, 1]) / 2.
+                    Y = np.vstack([X, arr[:, 2]]).T.tolist()
+                    str_ += '\n\\addplot3 [area plot] coordinates {'
+                    for x_ in Y:
+                        str_ += str((x_[0], j, x_[1]))
+                    str_ += '};\n'
+                    j += 1
+                i += 1
+    print(str_)
+    import pdb; pdb.set_trace()
+    return agg_keys
+
+
+def gen_tex_single_key(data, key):
[…]

### 2020-12-27 evaluator_coop.py
Add support for stun in evaluator_coop.

@@ -1,3 +1,5 @@
+import os
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '2'
 import sys
 import glob
 import pickle
@@ -23,6 +25,7 @@ def load(id_, cfg_id, base_cfg_id, return_dict):
             print(id__ % cfg_id)
             res.extend(list(glob.glob(id__ % cfg_id)))
     print('####################')
+    print(id_)
     print(res)
 
     coop_ratios = []
@@ -40,9 +43,12 @@ def load(id_, cfg_id, base_cfg_id, return_dict):
                 print('####################')
             # TODO DUBIOUS! Should we maybe add a [0] if there's no dead fishes?
 
-    ci = st.t.interval(0.95, len(coop_ratios)-1, loc=np.mean(coop_ratios), scale=st.sem(coop_ratios))
-    print('avg_coop_ratio:%d' % np.mean(coop_ratios))
-    return_dict[id_] = (np.mean(coop_ratios), ci)
+    if coop_ratios:
+        ci = st.t.interval(0.95, len(coop_ratios)-1, loc=np.mean(coop_ratios), scale=st.sem(coop_ratios))
+        print('avg_coop_ratio:%d' % np.mean(coop_ratios))
+        return_dict[id_] = (np.mean(coop_ratios), ci)
+    else:
+        return_dict[id_] = (0, (0, 0))
 
 
 def main(id_):
@@ -82,11 +88,49 @@ def main(id_):
         'i10_r10_s05': ['ma9_t*_i10_p150_r10_s05', 'ma9_t2000_i10_p150_r10_s05_sp200']
     }
 
+    cfg_ids_i5_stun = {
+        'i5_r4_s03': ['ma9_t*_i5_p150_r4_s03_stun_ext', 'ma9_t2000_i5_p150_r4_s03_stun_ext_sp200'],
+        'i5_r4_s035': ['ma9_t*_i5_p150_r4_s035_stun_ext', 'ma9_t3000_i5_p150_r4_s035_stun_ext_sp200'],
[…]

### 2020-12-27 network_models.py
Remove unnecessary print.

@@ -6,7 +6,7 @@ from baselines.common.models import register
 
 def mlp_norm(norm, num_layers=2, num_hidden=64, activation=tf.tanh):
     def network_fn(input_shape):
-        print('input shape is {}'.format(input_shape))
+        # print('input shape is {}'.format(input_shape))
 
         x_input = tf.keras.Input(shape=input_shape)
         h = x_input

### 2020-12-27 evaluator_dqn_comp.py
Add evaluator script for DQN comparison.

@@ -1,0 +1,35 @@
+import os
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '2'
+import numpy as np
+import scipy.stats as st
+
+
+def load(fname):
+    from pipeline import Experiment
+
+    tot_rewards = []
+    scenarios = [1, 2, 5, 10]
+    for scenario in scenarios:
+        print('Scenario', scenario)
+        for _ in range(100):
+            exp = Experiment('8_obs', show_gui=False, dump_cfg=False)
+            exp.env.select_fish_types(0, scenario, 0)
+            exp.load_eval(fname, steps=500, initial_survival_time=3000)
+            tot_rewards.append(10. * exp.env.dead_fishes)
+
+        ci = (0, 0)
+        if len(tot_rewards) > 1:
+            ci = st.t.interval(0.95, len(tot_rewards) - 1, loc=np.mean(tot_rewards), scale=st.sem(tot_rewards))
+        m = np.mean(tot_rewards)
+        print('avg_tot_rewards: %d +- %d' % (m, m - ci[0]))
+
+
+def main():
+    models = [
+        'models/8_obs-opal.cip.ifi.lmu.de-20.12.26-15:48:05-30316607-model-4'
+    ]
+    load(models[0])
+
+
+if __name__ == '__main__':
+    main()

### 2020-12-27 pipeline.pyx
Remove unnecessary prints.

@@ -44,6 +44,7 @@ from baselines.common.models import get_network_builder
 
 # Importing network models registers them.
 import network_models  # noqa
+import animal_controller
 from env.aquarium import Aquarium
 from env.shark import Shark
 from env.fish import Fish
@@ -328,6 +329,9 @@ class Experiment:
             )
         if self.use_random_fish_pop_curriculum:
             self.fish_pop_curriculum = [x[1] for x in self.cfg['aquarium']['fish_pop_curriculum']]
+
+        if self.cfg['aquarium']['turnaway_fish_use_two_sharks_for_repel']:
+            animal_controller.TurnAwayFishController.USE_TWO_SHARKS = True
 
         # High values increase acceleration, maximum speed and turning circle.
         Shark.FRICTION = self.cfg["aquarium"]["shark_friction"]

### 2020-12-27 env/animal_controller.pyx
Allow using two sharks in turnaway fish. Add new param configs using this, also fish has higher view distance.

@@ -119,6 +119,8 @@ class BoidFishController(Controller):
 
 
 class TurnAwayFishController(Controller):
+    USE_TWO_SHARKS = False
+
     @staticmethod
     def get_action(
             own_orientation: float,
@@ -133,6 +135,10 @@ class TurnAwayFishController(Controller):
 
         distance_to_shark = shark_observation[0]
         angle_to_shark = shark_observation[1]
+        # TODO: Added by instance01
+        if TurnAwayFishController.USE_TWO_SHARKS:
+            distance_to_shark2 = shark_observation[3]
+            angle_to_shark2 = shark_observation[4]
 
         distance_to_closest_fish = fish_observation[0]
         angle_to_closest_fish = fish_observation[1]
@@ -147,12 +153,16 @@ class TurnAwayFishController(Controller):
         current_vector = np.array(util.polar_to_cartesian(1.0, own_orientation))
         fish_force = calculate_repel_force(distance_to_closest_fish, angle_to_closest_fish)
         shark_force = calculate_repel_force(distance_to_shark, angle_to_shark)
+        if TurnAwayFishController.USE_TWO_SHARKS:
+            shark_force2 = calculate_repel_force(distance_to_shark2, angle_to_shark2)
         wall1_force = calculate_repel_force(distance_to_closest_wall, angle_to_closest_wall)
         wall2_force = calculate_repel_force(distance_to_second_closest_wall, angle_to_second_closest_wall)
         # TODO: Unused.
         # noise_force = np.array([random.uniform(-1, 1), random.uniform(-1, 1)])
 
         target_vector = current_vector + shark_force
+        if TurnAwayFishController.USE_TWO_SHARKS:
+            target_vector += shark_force2
         target_vector += 0.5 * fish_force
         target_vector += 0.5 * wall1_force + 0.3 * wall2_force
         angle = util.angle_of(target_vector)

### 2020-12-27 env/aquarium.pyx

@@ -403,7 +403,7 @@ class Aquarium:
                     max_dist = min(shark_.view_distance, self.max_animal_view_distance)
                     radius_dist = util.scale(self.kill_zone_radius, min_dist, max_dist, 0, OBSERVATION_MAX)
 
-                    print(dist, radius_dist)
+                    # print(dist, radius_dist)
                     if dist > radius_dist:
                         continue
 
@@ -426,7 +426,7 @@ class Aquarium:
                         reward_main_shark -= split_rew
                     else:
                         ratio = 1. - dist / radius_dist
-                        print(ratio)
+                        # print(ratio)
                         # TODO: To simplify, could consider integer only rewards.
                         # E.g.: round(ratio * 5)
                         # Right now it's floats.
@@ -451,7 +451,7 @@ class Aquarium:
 
             self.dead_fishes += 1
             shark.eaten_fish += 1
-            print('coop ratio', self.coop_kills / self.dead_fishes, 'full coop ratio', self.full_coop_kills / self.dead_fishes)
+            # print('coop ratio', self.coop_kills / self.dead_fishes, 'full coop ratio', self.full_coop_kills / self.dead_fishes)
 
     def _handle_stun_move(self, a1, a2):
         """Make a shark unable to move for a certain number of steps and turn it

### 2020-12-27 pipeline.pyx
Add a few missing param configs.

@@ -44,7 +44,7 @@ from baselines.common.models import get_network_builder
 
 # Importing network models registers them.
 import network_models  # noqa
-import animal_controller
+import env.animal_controller
 from env.aquarium import Aquarium
 from env.shark import Shark
 from env.fish import Fish
@@ -331,7 +331,7 @@ class Experiment:
             self.fish_pop_curriculum = [x[1] for x in self.cfg['aquarium']['fish_pop_curriculum']]
 
         if self.cfg['aquarium']['turnaway_fish_use_two_sharks_for_repel']:
-            animal_controller.TurnAwayFishController.USE_TWO_SHARKS = True
+            env.animal_controller.TurnAwayFishController.USE_TWO_SHARKS = True
 
         # High values increase acceleration, maximum speed and turning circle.
         Shark.FRICTION = self.cfg["aquarium"]["shark_friction"]

### 2021-01-04 plots/gen_inn_last_fish_pop_chart.py
Update fish pop chart

@@ -9,7 +9,8 @@ mpl.font_manager._rebuild()
 plt.rc('font', family='Raleway')
 
 
-with open('inn_last_fish_pop.pickle', 'rb') as f:
+# with open('../pickles/inn_last_fish_pop.pickle', 'rb') as f:
+with open('../pickles/t800_5fish_last_fish_pop.pickle', 'rb') as f:
     a = pickle.load(f)
 
 
@@ -18,25 +19,21 @@ def moving_average(x, w):
 
 
 a = moving_average(a, 100)
+print(len(a))
+
+plt.figure(figsize=(4, 3))
 plt.plot(a, linewidth=.8, c='#ffffff')
 plt.ylabel('Fish population at the end of an episode')
 plt.xlabel('Steps in million')
-plt.xticks([0, 1000, 2000, 3000, 4000, 5000, 6000], ['0', '2', '4', '6', '8', '10', '12'])
-# plt.axvspan(0, 600, facecolor='#990000', alpha=0.2)
-# plt.axvspan(600, 5100, facecolor='#009900', alpha=0.2)
-# plt.axvspan(5100, 5900, facecolor='#000099', alpha=0.2)
-# plt.axvspan(0, 600, facecolor='#344966', alpha=0.6)
-# plt.axvspan(600, 5100, facecolor='#2D7DD2', alpha=0.6)
-# plt.axvspan(5100, 5900, facecolor='#009440', alpha=0.7)
-plt.axvspan(0, 600, facecolor='#00622c', alpha=1.0)
-plt.axvspan(600, 5100, facecolor='#007a35', alpha=1.0)
-plt.axvspan(5100, 5900, facecolor='#009440', alpha=1.0)
-plt.axvline(600, color='black', linestyle='--' , linewidth=.2)
-plt.axvline(5100, color='black', linestyle='--', linewidth=.2)
+plt.xticks([0, 2000, 4000, 6000, 8000, 10000, 12000, 13980], ['0', '3', '6', '9', '12', '15', '18', '21'])
+plt.axvspan(0, 2000, facecolor='#00622c', alpha=1.0)
+plt.axvspan(2000, 4800, facecolor='#007a35', alpha=1.0)
+plt.axvspan(4800, 13980, facecolor='#009440', alpha=1.0)
+plt.axvline(2000, color='black', linestyle='--' , linewidth=.2)
+plt.axvline(4800, color='black', linestyle='--', linewidth=.2)
 plt.axhline(2, color='black', linestyle='--', linewidth=.5)
[…]

### 2021-01-04 plots/gen_plot_inn.py

@@ -1,0 +1,265 @@
+import tensorflow as tf
+import glob
+import sys
+import os
+from collections import defaultdict
+
+import numpy as np
+
+from tensorflow.core.util import event_pb2
+from tensorflow.python.lib.io import tf_record
+
+
+def my_summary_iterator(path):
+    for r in tf_record.tf_record_iterator(path):
+        yield event_pb2.Event.FromString(r)
+
+
+def smooth(y, box_pts):
+    box = np.ones(box_pts) / box_pts
+    y_smooth = np.convolve(y, box, mode='same')
+    return y_smooth
+
+
+def aggregate(path):
+    keys = [
+        # 'Train/Tot_Reward',
+        # 'Eval/Length',
+        # 'Eval/MCTS_Confidence',
+        # 'Train/AvgLoss'
+        # 'Eval/MCTS_Confidence'
+        'Train/Last_Fish_Population'
+    ]
+
+    agg_runs = defaultdict(lambda: defaultdict(list))
+    agg_keys = {}
+
+    path = glob.glob(os.path.join(path, "events.out.tfevents.*"))
+    if not path:
+        return None, None
+    path = path[0]
+
+    data  =[]
+    for event in my_summary_iterator(path):
+        if not event.summary.value:
+            continue
+        tag = event.summary.value[0].tag
+        for key in keys:
+            # if tag.startswith(key):
+            #     run = tag[tag.rfind('/')+1:]
+            #     val = tf.make_ndarray(event.summary.value[0].tensor)
+            #     agg_runs[key][run].append(val)
+            if key == tag:
+                val = float(tf.make_ndarray(event.summary.value[0].tensor))
+                # print(val)
+                data.append(val)
+
+    # data = smooth(data, 20)[10:-9]
+    # import pickle
+    # print(data)
+    # print(len(data))
+    # with open('t800_5fish_last_fish_pop.pickle', 'wb+') as f:
+    #     pickle.dump(data, f)
+    # import matplotlib.pyplot as plt
+    # plt.plot(data)
+    # plt.show()
+
+    for key in agg_runs:
+        aggregated = []
+        for run in agg_runs[key]:
+            aggregated.append(agg_runs[key][run])
+        max_len = max(len(x) for x in aggregated)
+        aggregated_ = []
+        for i, x in enumerate(aggregated):
+            aggregated_.append(
+                np.pad(
+                    x,
+                    (0, max_len - len(x)),
+                    mode='constant',
[…]

### 2021-01-04 paper/paper.tex
Add paper with blindtext and a few charts, also add figures for paper.

@@
 \usepackage{natbib,alifeconf}  %% The order is important
+\usepackage{graphicx}%
+\usepackage{blindtext}
+\usepackage{subfig}
 
@@
 
-\title{Critical Exponent of Species-Size Distribution in Evolution}
-\author{Chris Adami$^{1}$, Ryoichi Seki$^{1,2}$ \and Robel Yirdaw$^2$ \\
+\title{Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting}
+\title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
+\author{Daniel Ratke$^{2}$, Fabian Ritz$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
 \mbox{}\\
-$^1$California Institute of Technology, Pasadena, CA 91125 \\
-$^2$California State University, Northridge, CA 91330 \\
-adami@caltech.edu} % email of corresponding author
+$^1$Mobile and Distributed Systems Group, LMU Munich, Germany \\
+$^2$LMU Munich, Germany \\
+D.Ratke@campus.lmu.de} % email of corresponding author
 
@@
 % Abstract length should not exceed 250 words
-  We analyze the geometry of the species-- and genotype-size
-  distribution in evolving and adapting populations of single-stranded
-  self-replicating genomes: here programs in the Avida world.  We find
-  that a scale-free distribution (power law) emerges in complex
-  landscapes that achieve a separation of two fundamental time scales:
-  the relaxation time (time for population to return to equilibrium
-  after a perturbation) and the time between mutations that produce
-  fitter genotypes. The latter can be dialed by changing the mutation
-  rate.  In the scaling regime, we determine the
-  critical exponent of the distribution of sizes and strengths of
-  avalanches in a system without coevolution, described by first-order
-  phase transitions in single finite niches.
+    \blindtext[2]
 \end{abstract}
@@
 
-Power law distributions in Nature usually signal the absence of a
-scale in the region where the scaling is observed, and sometimes point
-to critical dynamics. In Self-Organized-Criticality (SOC)
-\citep{BTW87,BTW88}, for example, power law distributions reveal the
-dynamics of an unstable critical point, brought about by slow driving
-and a feed-back mechanism between order parameter and critical
-parameter.  The critical dynamics is usually described within the
-language of second-order phase transitions in condensed matter systems
-\citep{SJD}, but it can be shown that SOC-type behavior also occurs
-within a dual description in terms of the Landau-Ginzburg equation as
-{\em first-order} transitions \citep{GS}.  Indeed, it was shown that a
-power law distribution of {\em epoch-lengths}, that is, the time a
-particular species dominates the dynamics of an adapting population,
-is explained by a self-organized critical scenario \citep{CA2} that
-carries the hallmark of first-order phase transitions. Here, we
-measure the distribution of abundances of {\em species} and genotypes
-in an artificial chemistry, \citep[the Avida Artificial Life
-system][]{AB1,OBA} and show that the distribution is scale-free under
-a broad class of circumstances, confirming the results reported in
-\citep{CA2}.  In the next section, we discuss the first-order dynamics
-in more detail and examine ``avalanches of invention'' from the point
-of view of a thermodynamics of information. In Section III, we measure
-the critical exponent of the power law of genotype abundances in the
-limit of infinitesimal driving, i.e., infinitesimal mutation rate, and
-discuss the role of the fitness landscape in shaping the
-distribution. In Section IV, we repeat the analysis for a higher
-taxonomic level (that of species) and discuss its relation to the
-geometric distributions found by \citet{BUR90,BUR93}.
-Conclusions about the evolutionary process drawn from the data
-obtained in this paper are presented in Section V.
+\blindtext[3]
 
-\section{Self-Organization in Evolution}
+\begin{figure}%
+    \centering
+    \subfloat[][\centering Two predators and multiple prey]{\includegraphics[width=3.8cm]{figures/game_screen2.png} }%
+    \subfloat[][\centering A stunned predator]{\includegraphics[width=3.66cm]{figures/stun_move2.png} }%
+    \caption{The predator-prey environment, with yellow predators and blue prey. Predators can stun each other.}%
+    \label{fig:aquarium}%
+\end{figure}
 
-The idea that the evolutionary process occurs in spurts, jumps, and
-bursts rather than gradual, slow and continuous changes has been
-around for over 75 years \citep{WIL}, but has gained prominence as
-``punctuated equilibrium'' through the work of \citet{GE77,GE93}. The
-general idea is that evolutionary innovations are not bestowed upon an
-existing species as a whole, gradually, but rather by the emergence of
-{\em one} better adapted mutant which, by its superiority, serves as
-the seed of a new breed that sweeps through an ecological niche and
-supplants the species previously occupying it. The global dynamics
-thus has a microscopic origin, as shown experimentally, e.g., in
-populations of {\it E. Coli} \citep{ECL96}.
+\section{Background}
 
-Such avalanches can be viewed in two apparently contradictory ways. On
-the one hand we may consider the wave of extinction touching all
-species that are connected by their ecological relations, a process
-akin to percolation and therefore suitably described by the language
-of second-order critical phenomena \citep{BS}. Such a scenario relies
-on the {\em coevolution} of species (to build their ecological
-relations) and successfully describes power-law distributions obtained
-from the fossil record \citep{SB96,BP96}. There is, on the other hand,
-a description in terms of {\em informational} avalanches that does not
-require coevolution and leads to the same statistics, as we show
-here. Rather than contradicting the aforementioned picture
-\citep{NFST}, we believe it to be complementary.
+\subsection{Reinforcement Learning}
 
-In the following, we set up a scenario in which {\em information} is
-viewed as the agent of self-organization in evolving and adapting
-populations. Information is, in the strict sense of Shannon theory, a
-measure of correlation between two ensembles: here a population of
-genomes and the environment it is adapting to. As described elsewhere
-\citep{IAL}, this correlation grows as the population stores more and
-more information about the environment via random measurements,
-implementing a very effective {\em natural Maxwell demon}. Any time a
-stochastic event increases the information stored in the population, a
-wave of extinction removes the less adapted genomes and establishes a
-new era. Yet, information cannot leave the population as a whole,
-which therefore may be thought of as protected by a {\em
-semi-permeable membrane} for information, the hallmark of the Maxwell
-demon. Let us consider this dynamics in more detail.
+\blindtext[2]
 
-The simple living systems we consider here are populations of
-self-replicating strings of instructions, coded in an alphabet of
-dimension ${\cal D}$ with variable string length $\ell$. The total
-number of possible strings is exponentially large. Here, we consider
-the subset of all strings currently in existence in a finite
-population of size $N$, harboring $N_g$ different types, where
-$N_g\ll{\cal D}^\ell$. Each {\em genotype} (particular sequence of
-instructions) is characterized by its replication rate $\epsilon_i$,
-which depends on the sequence only, while its survival rate is given
-by $\epsilon_i/\langle \epsilon\rangle$, in a ``stirred-reactor''
-environment that allows a mean-field picture. This average replication
-rate $\langle \epsilon\rangle$ characterizes the fitness of the
-population as a whole, and is given by
-\begin{eqnarray}
-\langle \epsilon\rangle=\sum_i^{N_g}\frac{n_i}N \epsilon_i\;,
-\end{eqnarray}
-where $n_i$ is the {\em occupation number}, or frequency, of genotype
-$i$ in the population. As $N_g$ is not fixed in time, the average
-depends on time also, and is to be taken over all genotypes currently
-living. The total abundance, or size, of a genotype is then
-\begin{eqnarray}
-s_i=\int_0^\infty n_i(t)\, dt=\int_{T_c}^{T_e}n_i(t)\, dt\;,
-\label{size}
-\end{eqnarray}
-where $T_c$ is the time of creation of this particular genotype, and
-$T_e$ the moment of extinction. Before we obtain this distribution in
-Avida, let us delve further into the statistical description of the
-extinction events.
+\subsection{Multi-Agent Reinforcement Learning}
 
-At any point in time, the fate of every string in the population is
-determined by the craftiness of the best adapted member of the
-population, described by $\epsilon_{\rm best}$. In this simple,
-finite, world, which does not permit strings to affect other members
-of the population except by replacing them, not being the best reduces
-a string to an ephemeral existence. Thus, every string is
-characterized by a {\em relative} fitness, or {\em inferiority}
-\begin{eqnarray}
-E_i=\epsilon_{\rm best}-\epsilon_i
-\end{eqnarray}
-which plays the role of an {\em energy} variable for strings of
-information {IAL}. Naturally, $\langle E\rangle=0$ characterizes the
-{\em ground state}, or vacuum, of the population, and strings with
-$E_i>0$ can be viewed as occupying {\em excited} states, soon to
-``decay'' to the ground state (by being replaced by a string with
-vanishing inferiority). Through such processes, the dynamics of the
-system tend to minimize the average inferiority of the population, and
-the fitness landscape of replication rates thus provides a Lyapunov
-function. Consequently, we are allowed to proceed with our statistical
-analysis. Imagine a population in equilibrium, at minimal average
-inferiority as allowed by the ``temperature'': the rate (or more
-precisely, the probability) of mutation. Imagine further that a
-mutation event produces a new genotype, fitter than the others,
-exploiting the environment in novel ways, replicating faster than all
-the others. It is thus endowed with a new best replication rate,
-$\epsilon_{\rm best}^{\rm new}$, larger than the old ``best'' by an
-amount $\Delta \epsilon$, and redefining what it means to be
-inferior. Indeed, all inferiorities must now be {\em renormalized}:
-what passed as a ground state ($E=0$) string before now suddenly finds
-itself in an excited state. The seed of a new generation has been
-sown, a phase transition must occur. In the picture just described,
-this is a first-order phase transition with latent heat
-$\Delta\epsilon$ (see Fig.\ref{fig1}), starting at the ``nucleation''
-point, and leading to an expanding {\em bubble} of ``new phase''.
+\blindtext[2]
+
+\subsection{Herding Behaviour}
+
+\blindtext[2]
+
+\subsection{Cooperation}
+
+\blindtext[2]
+
+\subsection{Related Work}
+
+\blindtext[3]
+
+\section{Aquarium Environment}
+
+\blindtext[4]
+
+\section{Experimental Setup}
+
+\blindtext[2]
+
+\section{Results}
 
@@
 \begin{center}
-\includegraphics[width=2.1in,angle=-90]{fig1.eps}
-\caption{``Energies'' (inferiorities) of strings in a first-order
-  phase transition with latent heat $\Delta\epsilon$.}
-\label{fig1}
+\includegraphics[width=8cm]{figures/fish_pop_chart3.png}
+\caption{Left-over fish population per learning episode over 12M steps}
+\label{fig:fish_pop}
 \end{center}
@@
 
-This bubble expands with a speed given by the Fisher velocity
-\begin{eqnarray}
-v\sim\sqrt{D\Delta\epsilon}\;, \label{eq4}
-\end{eqnarray}
-where $D$ is the diffusion coefficient (of information) in this
-medium, until the entire population has been converted \citep{CHU}.
-This marks the end of the phase transition, as the population returns
-to equilibrium via mutations acting on the new species, creating new
-diversity and restoring the {\em entropy} of the population to its
-previous value. This prepares the stage for a new avalanche, as only
-an equilibrated population is vulnerable to even the smallest
-perturbation. The system has returned to a critical point, driven by
-mutations, self-organized by information.
-
-Thus we see how a first-order scenario, without coevolution, can lead
-to self-organized and critical dynamics. It takes place within a
-single, finite, ecological niche, and thus does not contradict the
-dynamics taking place for populations that span many niches. Rather,
-we must conclude that the descriptions complement each other, from the
-single-niche level to the ecological web. Let us now take a closer
-look at the statistics of avalanches in this model, i.e., at the
-distribution of genotype sizes.
-
-\section{Exponents and Power Laws}
-
-\hyphenation{ap-proximated}
-
-In this particular system avalanche size can be approximated
-by the size $s$ of the genotype that gave rise to it,
-Eq.~(\ref{size}).  We shall measure the distribution of these sizes
-$P(s)$ in the Artificial Life system Avida, which implements a
-population of self-replicating computer programs written in a simple
-machine language-like instruction set of ${\cal D}=24$ instructions,
-with programs of varying sequence length. In the course of
-self-replication, these programs produce mutant off-spring because the
-{\tt copy} instruction they use is flawed at a rate $R$ errors per
-instruction copied, and adapt to an environment in which the
-performance of {\em logical} computations on externally provided
-numbers is akin to the catalysis of chemical reactions \citep{OBA}. In
-this {\em artificial chemistry} therefore, successful computations
-accelerate the metabolism (i.e., the CPU) of those strings that carry
-the {\em gene} (code) necessary to perform the trick, and any program
-discovering a new trick is the seed of another avalanche.
-
-Avida is not a stirred-reactor environment (although one can be
-simulated). Rather, the programs live on a two-dimensional grid, each
-program occupying one site. The size of the grid is finite, and chosen
-in these experiments to be small enough that avalanches are generally
-over before a new one starts. As is well-known, this is the condition
-{\em sine qua non} for the observation of SOC behavior, a separation
-of time scales which implies that the system is driven at
-infinitesimal rates.
-
-Let $\tau$ denote the average duration of an avalanche. Then, a
-separation of time scales occurs if the average time between the
-production of new seeds of avalanches is much larger than $\tau$. New
-seeds, in turn, are produced with a frequency $\langle\epsilon\rangle
-P$, where $\langle\epsilon\rangle$ is again the average replication
-rate, and $P$ is the mutation probability (per replication period) for
-an average sequence of length $\ell$,
-\begin{eqnarray}
-P=1-(1-R)^\ell\;.
-\end{eqnarray}
-For small enough $R$ and not too large $\ell$ (so that the product
-$R\ell$ is smaller than unity) we can approximate
-$P\approx R\ell$, and infinitesimal driving occurs in the limit
-\begin{eqnarray}
-\langle \epsilon\rangle R\ell \ll\frac1\tau\;.\label{cond}
-\end{eqnarray}
-Furthermore
-\begin{eqnarray}
-\tau\sim\frac{L}v
-\end{eqnarray}
-with $L$ the diameter of the system and $v$ a typical Fisher velocity.
-The fastest waves are those for which the latent heat is of the order
-of the new fitness, i.e., $\Delta\epsilon\sim\epsilon$, in which case
-$v\approx \epsilon$ \citep[because $D\sim\epsilon$ in
-Eq.~(\ref{eq4}),][]{CHU}, and a separation of time scales is assured
-whenever
-\begin{eqnarray}
-\frac1{R\ell}\gg {L}\;,
-\end{eqnarray}
-that is, in the limit of vanishing mutation rate or small population
-sizes. For the $L=60$ system used here, this condition is obeyed (for
-the fastest waves) only for the smallest mutation rate tested and
-sequence lengths of the order of the ancestor.
-
 \begin{figure}[t]
-\includegraphics[width=2.3in, angle=90]{fig2.eps}
-\caption{Fitness of the dominant genotype in the population, $\epsilon_{\rm best}$ as a function of time (in updates).}
-\label{fig2}
-\end{figure}
-
-In the following, we keep the population size constant (a $60\times60$
-grid) and vary the mutation rate. From the previous arguments, we
-expect true scale-free dynamics only to appear in the limit of small
-mutation rates.  As in this limit avalanches occur less and less
-frequently, this is also the limit where data are increasingly
-difficult to obtain, and other finite size effects can come into play.
-We shall try to isolate the scale-free regime by fitting the
-distribution to a power law
-\begin{eqnarray}
-P(s)\sim s^{-D(R)}\label{power}
-\end{eqnarray}
-and monitor the behavior of $D$ from low to high mutation rates.
-
-In Fig.~\ref{fig2}, we display a typical history of $\epsilon_{\rm
-best}$, i.e., the fitness of the dominant genotype.\footnote{As the
-replication rate $\epsilon$ is exponential in the bonus obtained for a
-successful computation, $\epsilon_{\rm best}$ increases exponentially
-with time.}  Note the ``staircase'' structure of the curve reflecting
-the ``punctuated'' dynamics, where each step reflects a new avalanche
-and concurrently an extinction event. Staircases very much like these
-are also observed in adapting populations of {\it E. Coli}
-\citep{LT94}.
-
-As touched upon earlier, the Avida world represents an environment
-replete with information, which we encode by providing bonuses for
-performing logical computations on externally provided (random)
-numbers. The computations rewarded usually involve two inputs $A$ and
-$B$, are finite in number and listed in Table~1. At the end of a
-typical run (such as Fig.~\ref{fig2}) the population of programs is
-usually proficient in almost all tasks for which bonuses are given
-out, and the genome length has grown to several multiples of the
-initial size to accommodate the acquired information.
-
-\begin{table}[h]
-\center{
-\begin{tabular}{|c|c|c|c|}\hline
-Name & Result & Bonus $b_i$ & Difficulty\\ \hline\hline
-Echo & I/O   & 1 & --\\
-Not  & $\neg A$ & 2 & 1 \\
-Nand & $\neg(A\wedge B)$ & 2 & 1 \\
-Not Or & $\neg A \vee B$ & 3 & 2 \\
-And  &  $ A \wedge B $   & 3 & 2 \\
-Or   &  $ A \vee B $     & 4 & 3 \\
-And Not & $A\wedge\neg B$& 4 & 3 \\
-Nor  & $\neg(A\vee B)$   & 5 & 4 \\
-Xor  & $ A\ {\rm xor}\ B$ &   6 & 4 \\
-Equals &$\neg(A\ {\rm xor}\ B)$&6& 4 \\ \hline
-\end{tabular}
-}
-\vskip 0.25cm
-\caption{Logical calculations on random inputs $A$ and $B$ rewarded,
-bonuses, and difficulty (in minimum number of {\tt nand} instructions
-required). Bonuses $b_i$ increase the speed of a CPU by a factor
-$\nu_i=1+2^{b_i-3}$.}
-\end{table}
-
-Because the amount of information stored in the landscape is finite,
-adaptation, and the associated avalanches, must stop when the
-population has exhausted the landscape.  However, we shall see that
-even a `flat' landscape (on which evolution is essentially neutral
-after the sequence has optimized its replicative strategy) gives rise
-to a power law of genotype sizes, as long as the programs do not
-harbor an excessive amount of ``junk'' instructions.  A typical
-abundance distribution (for the run depicted in Fig.~\ref{fig2}) is
-shown in Fig.~\ref{fig3}.
-
-\begin{figure}[ht]
 \begin{center}
-\includegraphics[width=2.25in, angle=90]{fig3.eps}
-\caption{Distribution of genotypes sizes $P(s)$ fitted to a power law
-  (solid line) at mutation rate $R=0.004$.}
-\label{fig3}
+\includegraphics[width=6cm]{figures/shark_speeds.png}
+\caption{Distribution of shark speeds over time}
+\label{fig:shark_speeds}
 \end{center}
@@
 
-As mentioned earlier, we can also turn {\em off} all bonuses listed in
-Tab.~1, in which case fitness is related to replicative abilities
-only. Still, avalanches occur (within the first 50,000 updates
-monitored) due to minute improvements in fitness, but the length of
-the genomes typically stays in the range of the ancestor, a program of
-length 31 instructions. We expect a change of dynamics once the
-``true'' maximum of the local fitness landscape is reached, however,
-we did not reach this regime in the experiments presented here. The
-distribution of genotype sizes for the flat landscape is depicted in
-Fig.~\ref{fig4}.
+\blindtext[8]
 
-\begin{figure}[!tbp]
-\begin{center}
-\includegraphics[width=2.25in, angle=90]{fig4.eps}
-\caption{Distribution of genotypes sizes $P(s)$ for a landscape devoid
-  of the bonuses listed in Tab.~1, at mutation rate $R=0.003$.} \label{fig4}
-\end{center}
-\end{figure}
+\section{Conclusion}
 
-Clearly then, even such landscapes (flat with respect to all other
-activities except replication) are not neutral. Indeed, it is known
-that neutral evolution, where the chance for a genotype to increase or
-decrease in number is even, leads to a power law in the abundance
-distribution with exponent $D=1.5$ \citep{ABH}.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=2.2in, angle=90]{fig5.eps}
-\vskip 0.25cm
-\caption{Fitted exponent of power law for 34 runs at mutation rates
-  between $R=0.0005$ and $R=0.01$ copy errors per instruction
-  copied. The error bars reflect the standard deviation across the
-  sample of runs taken at each mutation rate. The solid line is to
-  guide the eye only.
-}
-\label{fig5}
-\end{center}
-\end{figure}
-
-In order to test the dependence of the fitted exponent $D(R)$
-[Eq.~(\ref{power})] on the mutation rate, we conduct a set of
-experiments at varying copy-mutation rates from $0.5\times10^{-3}$ to
-$10\times10^{-3}$ and take data for 50,000 updates. Again, a ``best''
-genotype is not reached after this time, and we must assume that
-avalanches were still occurring at the end of these runs. Furthermore,
-in some runs we find that a genotype comes to dominate the population
-(usually after most `genes' have been discovered) which carries an
-unusual amount of junk instructions. As mentioned earlier, such
-species produce a distribution that is exponentially suppressed at
-large genotype sizes (data not shown). To avoid contamination from
-such species, we stop recording genotypes after a plateau of fitness
-was reached, i.e., if the population had discovered most of the
-bonuses. Furthermore, in order to minimize finite size effects on the
-determination of the critical exponent, we excluded from this fit all
-genotype abundances larger than 15, i.e., we only fitted the smallest
-abundances. Indeed, at larger mutation rates the higher abundances are
-contaminated by a pile-up effect due to the toroidal geometry, while
-at lower mutation rates a scale appears to enter which prevents
-scale-free behavior. We have not, as yet, been able to determine the
-origin of this scale.
-
-In the results reported here, we show the dependence of the fitted
-exponent $D$ as a function of the mutation rate $R$ used in the run,
-which, however, is a good measure of the mutation probability $P$ only
-at small $R$ and if the sequence length is not excessive. As a
-consequence, data points at large $R$, as well as runs where an
-excessive sequence length developed, carry a systematic error.
-
-\section{Acknowledgements}
-
-This work was supported by NSF grant No.\ PHY-9723972.
+\blindtext[2]
 

### 2021-01-05 visualize_coop.py
visualize_coop.py now supports separate figures

@@ -72,43 +72,74 @@ print(i10_data)
 print(i5_data)
 
 
-# y_labels = ['r4', 'r6', 'r10']
-# x_labels = ['s03', 's035', 's04', 's05']
-y_labels = ['4', '6', '10']
-x_labels = ['.03', '.035', '.04', '.05']
+def plot(data, label_data):
+    y_labels = ['4', '6', '10']
+    x_labels = ['.03', '.035', '.04', '.05']
 
-cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
-# fig, (ax, ax2) = plt.subplots(1, 2, figsize=(5,3.3))
-# fig, (ax, ax2) = plt.subplots(1, 2, figsize=(10, 6.5))
-# fig, (ax, ax2) = plt.subplots(1, 2, figsize=(6, 2.2), constrained_layout=True)
-fig, (ax, ax2) = plt.subplots(1, 2, figsize=(6, 2.0), constrained_layout=True)
-im = ax.imshow(i10_data, cmap=cmap_mod)
-im2 = ax2.imshow(i5_data, cmap=cmap_mod)
+    cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
+    fig, ax = plt.subplots(1, 1, figsize=(3.5, 2.0), constrained_layout=True)
+    im = ax.imshow(data, cmap=cmap_mod)
 
-# Colorbar
-cbar = ax.figure.colorbar(im, ax=[ax, ax2])
-cbar.ax.set_ylabel('Avg Coop Ratio', rotation=-90, va="bottom")
+    # Colorbar
+    cbar = ax.figure.colorbar(im, ax=ax)
+    cbar.ax.set_ylabel('Avg Coop Ratio', rotation=-90, va="bottom")
 
-# Ticks and labels
-ax.set_xticks(np.arange(len(x_labels)))
-ax.set_yticks(np.arange(len(y_labels)))
-ax.set_xticklabels(x_labels)
-ax.set_yticklabels(y_labels)
-ax2.set_xticks(np.arange(len(x_labels)))
-ax2.set_yticks(np.arange(len(y_labels)))
-ax2.set_xticklabels(x_labels)
-ax2.set_yticklabels(y_labels)
-ax.set_ylabel('Killzone Radius', rotation=90, va="bottom")
-ax.set_xlabel('Shark speed', rotation=0, va="top")
[…]

### 2021-01-05 plots/gen_dqn_comp_chart2.py
Minor plotting fixes

@@ -95,7 +95,7 @@ def bar_plot(
 
 def plot(data, err_data, data2, err_data2):
     scenarios = [100, 200, 300]
-    fig, ax = plt.subplots()
+    fig, ax = plt.subplots(figsize=(4, 3.5))
     bar_plot(
         ax,
         data,
@@ -113,7 +113,7 @@ def plot(data, err_data, data2, err_data2):
     imagebox.image.axes = ax
     xy = [0.3, 22]
     ab = AnnotationBbox(imagebox, xy,
-                        xybox=(110., 10.),
+                        xybox=(50., 0.),
                         xycoords='data',
                         boxcoords="offset points",
                         pad=0.1,
@@ -133,7 +133,7 @@ def plot(data, err_data, data2, err_data2):
     imagebox.image.axes = ax
     xy = [0.3, 8]
     ab = AnnotationBbox(imagebox, xy,
-                        xybox=(110., 60.),
+                        xybox=(50., 50.),
                         xycoords='data',
                         boxcoords="offset points",
                         pad=0.1,
@@ -151,6 +151,7 @@ def plot(data, err_data, data2, err_data2):
     plt.xlabel('Time until reproduction possible')
     plt.ylabel('Sustainability')
     plt.xlim(-0.5, 2.5)
+    plt.tight_layout()
     plt.show()
 
 

### 2021-01-05 visualize_coop_starve.py

@@ -71,13 +71,13 @@ def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_da
     x_labels = ['.03', '.04', '.05']
 
     cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
-    fig, (ax, ax2, ax3) = plt.subplots(1, 3, figsize=(6, 2.0), constrained_layout=True)
+    fig, (ax, ax2, ax3) = plt.subplots(1, 3, figsize=(6.5, 2.0), constrained_layout=True)
     im = ax.imshow(i5_data, cmap=cmap_mod)
     im2 = ax2.imshow(i5_data2, cmap=cmap_mod)
     im3 = ax3.imshow(i5_data3, cmap=cmap_mod)
 
     # Colorbar
-    cbar = ax.figure.colorbar(im, ax=[ax, ax2, ax3])
+    cbar = ax.figure.colorbar(im, ax=[ax, ax2, ax3], aspect=40)
     cbar.ax.set_ylabel('Avg Coop Ratio', rotation=-90, va="bottom")
 
     # Ticks and labels

### 2021-01-05 paper/paper.tex
Recompile paper with new figures

@@
 
-\blindtext[3]
+\blindtext[4]
 
@@
 
-\blindtext[2]
+\blindtext[3]
 
@@
 
-\blindtext[3]
+\blindtext[5]
 
@@
 
-\blindtext[4]
+\blindtext[5]
 
@@
 \begin{center}
+\includegraphics[width=8cm]{figures/dqncomp1fish_2.png}
+\caption{Sustainability of static, static-wait, DQN Stage II and PPO with initial fish population of 1.}
+\label{fig:dqncomp1}
+\end{center}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=8cm]{figures/dqncomp2fish_2.png}
+\caption{Sustainability of static, static-wait, DQN Stage II and PPO with initial fish population of 2.}
+\label{fig:dqncomp2}
+\end{center}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
 \includegraphics[width=8cm]{figures/fish_pop_chart3.png}
-\caption{Left-over fish population per learning episode over 12M steps}
+\caption{Left-over fish population per learning episode over 12M steps.}
 \label{fig:fish_pop}
@@
 \includegraphics[width=6cm]{figures/shark_speeds.png}
-\caption{Distribution of shark speeds over time}
+\caption{Distribution of shark speeds over time.}
 \label{fig:shark_speeds}
@@
 
-\blindtext[8]
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=8cm]{figures/Sterberisiko_vs_Herding_Two_Net_2.png}
+\caption{TODO : Placeholder Chart (Idea: Three distributions with fish pop i10,i5,i2)}
+\label{fig:herding}
+\end{center}
+\end{figure}
+
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/coop_movie_frames2.png}
+\caption{From left to right: Two sharks cooperatively catch a fish.}
+\label{fig:coop_movie}
+\end{center}
+\end{figure*}
+
+\begin{figure*}%
+    \centering
+    \subfloat[][\centering Cooperation rate with initial fish population of 10.]{\includegraphics[width=5.5cm]{figures/coop_chart_split1.png} }%
+    \subfloat[][\centering Cooperation rate with initial fish population of 5.]{\includegraphics[width=5.5cm]{figures/coop_chart_split2.png} }%
+    \subfloat[][\centering Cooperation rate with initial fish population of 5 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
+    \caption{Cooperation rate in different scenarios.}%
+    \label{fig:coop}%
+\end{figure*}
+
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=14cm]{figures/coop_vs_sterberisiko_5fish.png}
+\caption{Cooperation rate vs starving pressure with initial fish population of 5.}
+\label{fig:coop_starve}
+\end{center}
+\end{figure*}
+
+\blindtext[14]
 

### 2021-01-05 evaluator_corr_ppo.py
Add evaluator_corr_ppo.py

@@ -1,0 +1,77 @@
+import sys
+import os
+import multiprocessing
+from multiprocessing import Process
+import numpy as np
+import scipy.stats as st
+
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '2'
+
+from pipeline import Experiment
+
+
+MAX_STEPS = 3000
+# 8_obs_rand is for 100sp
+# 8_obs_rand_sp200
+# 8_obs_rand_sp300
+# 8_obs_rand_sp400
+# 8_obs_rand_sp500
+# 8_obs_rand_sp600
+#BASE_CFG = '8_obs_rand_sp600'
+BASE_CFG = sys.argv[1]
+
+
+def load(fname, scenario, ret_steps_til_first_kill, ret_fish_pop):
+    for _ in range(10):
+        exp = Experiment(BASE_CFG, show_gui=False, dump_cfg=False)
+        exp.env.select_fish_types(0, scenario, 0)
+        _, _ = exp.load_eval(fname, steps=MAX_STEPS, initial_survival_time=3000)
+        ret_steps_til_first_kill.append(exp.env.steps_til_first_kill)
+        ret_fish_pop.append(len(exp.env.fishes))
+
+
+def run(fnames):
+    print('EVALUATING WITH MAX_STEPS ', MAX_STEPS)
+    print('EVALUATING WITH BASECFG', BASE_CFG)
+
+    scenarios = [1]
+    for scenario in scenarios:
+        print('Scenario', scenario)
+
+        manager = multiprocessing.Manager()
+        steps_til_first_kill = manager.list()
+        fish_pop = manager.list()
+        procs = []
+        for fname in fnames:
+            p = Process(target=load, args=(fname, scenario, steps_til_first_kill, fish_pop))
+            p.start()
+            procs.append(p)
+        for p in procs:
+            p.join()
+
+        ci = st.t.interval(0.95, len(fish_pop) - 1, loc=np.mean(fish_pop), scale=st.sem(fish_pop))
+        m = np.mean(fish_pop)
+        print('avg_tot_rewards_pops: %f +- %f' % (round(m, 2), round(m - ci[0], 2)))
+        ci = st.t.interval(0.95, len(steps_til_first_kill) - 1, loc=np.mean(steps_til_first_kill), scale=st.sem(steps_til_first_kill))
[…]

### 2021-01-06 pipeline.pyx
Add evaluate_static and evaluate_static_wait to pipeline.

@@ -48,6 +48,7 @@ import env.animal_controller
 from env.aquarium import Aquarium
 from env.shark import Shark
 from env.fish import Fish
+from env.animal_controller import DefaultSharkController as DShark
 from custom_logger import Logger
 from custom_logger import EvolutionLogger
 from config import Config
@@ -623,6 +624,53 @@ class Experiment:
             # if i % 100 == 0:
             #     print(i, tot_rew)
         # print(i, tot_rew)
+        return rewards
+
+    def evaluate_static(self, steps=1000, initial_survival_time=3000):
+        self.env.env.max_steps = steps
+        Shark.INITIAL_SURVIVAL_TIME = initial_survival_time
+        self.env.env.seed = int(np.random.random() * 1e9)
+
+        """Run an evaluation game."""
+        obs = self.env.reset()
+        i = 0
+        rewards = []
+        tot_rew = 0
+        while not self.env.env.is_finished:
+            i += 1
+            action = DShark.get_action(**self.env.prepare_observation_for_controller(obs))
+            obs, reward, done, info = self.env.step([action], 'm1')
+            if self.show_gui:
+                self.env.env.render()
+            rewards.append(reward)
+            tot_rew += reward
+            if done:
+                break
+        return rewards
+
+    def evaluate_static_wait(self, steps=1000, initial_survival_time=3000):
+        self.env.env.max_steps = steps
+        Shark.INITIAL_SURVIVAL_TIME = initial_survival_time
+        self.env.env.seed = int(np.random.random() * 1e9)
+
+        """Run an evaluation game."""
+        obs = self.env.reset()
+        i = 0
+        rewards = []
+        tot_rew = 0
+        while not self.env.env.is_finished:
+            i += 1
+            if len(self.env.fishes) <= 1:
+                action = (0., 0., False)
+            else:
+                action = DShark.get_action(**self.env.prepare_observation_for_controller(obs))
+            obs, reward, done, info = self.env.step([action], 'm1')
+            if self.show_gui:
+                self.env.env.render()
+            rewards.append(reward)
+            tot_rew += reward
+            if done:
+                break
         return rewards
 
     def evaluate_and_log(self, model, n_episode):

### 2021-01-06 evaluator_herding.py
Add i2 to evaluator_herding.py

@@ -4,9 +4,12 @@ import pickle
 import multiprocessing
 from multiprocessing import Process
 from collections import OrderedDict
+from pipeline import Experiment
 
 
 def load(id_, cfg_id, return_dict):
+    # base_cfg_id = 'ma3_obs'  # for i10, i5 (sp600)
+    # base_cfg_id = 'ma3_obs_sp100'  # for i2
     base_cfg_id = 'ma3_obs'
     base_paths = ['models', 'modelsDec10-14', 'modelsDec15-20']
     res = []
@@ -25,15 +28,20 @@ def load(id_, cfg_id, return_dict):
             fname = fname[:-3]
         print('#############################')
         print(fname)
-        from pipeline import Experiment
         for _ in range(3):
-            fish_pop_hist, _ = Experiment(base_cfg_id, show_gui=False, dump_cfg=False).load_eval(fname, steps=5000)
+            exp = Experiment(base_cfg_id, show_gui=False, dump_cfg=False)
+            fish_pop_hist, _ = exp.load_eval(fname, steps=5000)
             if fish_pop_hist[-1] > 0 and fish_pop_hist[-1] < 10:
                 counter_coop += 1
             if fish_pop_hist[-1] == 0:
                 counter_greedy += 1
             if fish_pop_hist[-1] >= 10:
                 counter_fail += 1
+
+            # TODO: For i2 !
+            # if fish_pop_hist[-1] > 0 and exp.env.dead_fishes > 0:
+            #     counter_coop += 1
+            # print(exp.env.dead_fishes)
 
         total = counter_coop + counter_greedy + counter_fail
         print('c:%d' %counter_coop, 'f:%d' % counter_fail, 'g:%d' % counter_greedy, 't:%d' % total)
@@ -104,6 +112,20 @@ def main(id_):
         't2000': 'ma3_obs_starve_maxsteps_t2000_p150_5fish'
     }
 
+    cfg_ids_i2_p150 = {
+        't200': 'ma3_obs_starve_maxsteps_t200_i2_p150',
+        't300': 'ma3_obs_starve_maxsteps_t300_i2_p150',
+        't400': 'ma3_obs_starve_maxsteps_t400_i2_p150',
+        't500': 'ma3_obs_starve_maxsteps_t500_i2_p150',
+        't600': 'ma3_obs_starve_maxsteps_t600_i2_p150',
[…]

### 2021-01-06 custom_logger.pyx
A few miscellaneous changes

@@ -46,6 +46,7 @@ class Logger:
             tf.summary.scalar(prefix + '/Last_Fish_Population', fish_pop[-1], n_episode)
             tf.summary.scalar(prefix + '/Last_Shark_Population', shark_pop[-1], n_episode)
             tf.summary.scalar(prefix + '/Coop_Kills', env.coop_kills, n_episode)
+            # print('fc', env.full_coop_kills)
             if env.dead_fishes > 0:
                 coop_kills_ratio = env.coop_kills / env.dead_fishes
                 full_coop_kills_ratio = env.full_coop_kills / env.dead_fishes

### 2021-01-06 evaluator_coop_starve.py

@@ -53,40 +53,40 @@ def main(id_):
     multiprocessing.set_start_method('spawn')
 
     cfg_ids_i5 = {
-        # 't2000_i5_r4_s03': ['ma9_t2000_i5_p150_r4_s03_stun_ext', 'ma9_t3000_i5_p150_r4_s03_stun_ext'],
-        # 't2000_i5_r4_s04': ['ma9_t2000_i5_p150_r4_s04_stun_ext', 'ma9_t3000_i5_p150_r4_s04_stun_ext'],
-        # 't2000_i5_r4_s05': ['ma9_t2000_i5_p150_r4_s05_stun_ext', 'ma9_t3000_i5_p150_r4_s05_stun_ext'],
-        # 't2000_i5_r6_s03': ['ma9_t2000_i5_p150_r6_s03_stun_ext', 'ma9_t3000_i5_p150_r6_s03_stun_ext'],
-        # 't2000_i5_r6_s04': ['ma9_t2000_i5_p150_r6_s04_stun_ext', 'ma9_t3000_i5_p150_r6_s04_stun_ext'],
-        # 't2000_i5_r6_s05': ['ma9_t2000_i5_p150_r6_s05_stun_ext', 'ma9_t3000_i5_p150_r6_s05_stun_ext'],
-        # 't2000_i5_r10_s03': ['ma9_t2000_i5_p150_r10_s03_stun_ext', 'ma9_t3000_i5_p150_r10_s03_stun_ext'],
-        # 't2000_i5_r10_s04': ['ma9_t2000_i5_p150_r10_s04_stun_ext', 'ma9_t3000_i5_p150_r10_s04_stun_ext'],
-        't2000_i5_r10_s05': ['ma9_t2000_i5_p150_r10_s05_stun_ext', 'ma9_t3000_i5_p150_r10_s05_stun_ext']
+        't2000_i5_r4_s03': ['ma9_t2000_i5_p150_r4_s03_stun_ext', 'ma9_t3000_i5_p150_r4_s03_stun_ext'],
+        't2000_i5_r4_s04': ['ma9_t2000_i5_p150_r4_s04_stun_ext', 'ma9_t3000_i5_p150_r4_s04_stun_ext'],
+        't2000_i5_r4_s05': ['ma9_t2000_i5_p150_r4_s05_stun_ext', 'ma9_t3000_i5_p150_r4_s05_stun_ext'],
[…]

### 2021-01-06 gen_plot.py

@@ -24,11 +24,11 @@ def smooth(y, box_pts):
 def aggregate(path):
     keys = [
         # 'Train/Tot_Reward',
-        'Train/Last_Fish_Population',
         # 'Eval/Length',
         # 'Eval/MCTS_Confidence',
         # 'Train/AvgLoss'
         # 'Eval/MCTS_Confidence'
+        'Train/Last_Fish_Population'
     ]
 
     agg_runs = defaultdict(lambda: defaultdict(list))
@@ -38,15 +38,31 @@ def aggregate(path):
     if not path:
         return None, None
     path = path[0]
+
+    data  =[]
     for event in my_summary_iterator(path):
         if not event.summary.value:
             continue
         tag = event.summary.value[0].tag
         for key in keys:
-            if tag.startswith(key):
-                run = tag[tag.rfind('/')+1:]
-                val = tf.make_ndarray(event.summary.value[0].tensor)
-                agg_runs[key][run].append(val)
+            # if tag.startswith(key):
+            #     run = tag[tag.rfind('/')+1:]
+            #     val = tf.make_ndarray(event.summary.value[0].tensor)
+            #     agg_runs[key][run].append(val)
+            if key == tag:
+                val = float(tf.make_ndarray(event.summary.value[0].tensor))
+                # print(val)
+                data.append(val)
+
+    # data = smooth(data, 20)[10:-9]
+    # import pickle
+    # print(data)
+    # print(len(data))
+    # with open('t800_5fish_last_fish_pop.pickle', 'wb+') as f:
+    #     pickle.dump(data, f)
+    # import matplotlib.pyplot as plt
+    # plt.plot(data)
+    # plt.show()
 
     for key in agg_runs:
         aggregated = []
@@ -65,12 +81,6 @@ def aggregate(path):
             )
         agg_keys[key] = np.array(aggregated_)
 
-    # Lol. Used it for the fish population chart for the paper.
-    # import pickle
-    # a = [float(x) for x in agg_runs['Train/Last_Fish_Population']['Last_Fish_Population']]
-    # with open('a.pickle', 'wb+') as f:
-    #     pickle.dump(a, f)
-    # import pdb; pdb.set_trace()
     return agg_runs, agg_keys
 
 

### 2021-01-09 paper/paper.tex
Change order of authors
Add new herding plot

@@
 \title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
-\author{Daniel Ratke$^{2}$, Fabian Ritz$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
+\author{Fabian Ritz Ratke$^{1}$, Daniel Ratke$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
 \mbox{}\\
@@
     \subfloat[][\centering A stunned predator]{\includegraphics[width=3.66cm]{figures/stun_move2.png} }%
-    \caption{The predator-prey environment, with yellow predators and blue prey. Predators can stun each other.}%
+    \caption{The predator-prey environment, with yellow predators and blue prey. Predators can stun each other --- a stunned predator appears purple and cannot move for a certain number of steps.}%
     \label{fig:aquarium}%
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
 \begin{center}
-\includegraphics[width=8cm]{figures/Sterberisiko_vs_Herding_Two_Net_2.png}
-\caption{TODO : Placeholder Chart (Idea: Three distributions with fish pop i10,i5,i2)}
+\includegraphics[width=\textwidth]{figures/herding.png}
+\caption{TODO}
 \label{fig:herding}
 \end{center}
-\end{figure}
+\end{figure*}
 

### 2021-01-09 plots/gen_herding_distr_plot.py

@@ -1,0 +1,71 @@
+import pickle
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+from scipy.optimize import curve_fit
+
+
+mpl.font_manager._rebuild()
+plt.rc('font', family='Raleway')
+
+
+base_path = '../pickles/'
+
+with open(base_path + 'i10_p150_two_net_herding.pickle', 'rb') as f:
+    i10_p150 = pickle.load(f)
+with open(base_path + 'i5_p150_two_net_herding.pickle', 'rb') as f:
+    i5_p150 = pickle.load(f)
+with open(base_path + 'i2_p150_sp500_two_net_herding.pickle', 'rb') as f:
+    i2_p150 = pickle.load(f)
+
+
+print(i10_p150)
+print(i5_p150)
+print(i2_p150)
+
+
+def func(x, a, b, c, d, e):
+    return a + b * x + c * x**2 + d * x**3 + e * x**4
+
+
+# Three plots.
+fig, axs = plt.subplots(1, 3, figsize=(9, 3), sharey=True)
+
+axs[0].set_title('10 initial fishes')
+axs[0].set_ylabel('Herding Rate')
+axs[0].set_xlabel('Initial shark survival time t * 100')
+x = [str(int(x[1:]) // 100) for x in i10_p150[0]]
+y = [x[0] for x in i10_p150[1]]
+axs[0].bar(x, y, color='#009440')
+x = np.arange(len(y))
+fittedParameters, pcov = curve_fit(func, x, y)
+y_fit = func(x, *fittedParameters)
+axs[0].plot(x, y_fit, 'k:')
+
+
+axs[1].set_title('5 initial fishes')
+# axs[1].set_ylabel('Herding Rate')
+axs[1].set_xlabel('Initial shark survival time t * 100')
+x = [str(int(x[1:]) // 100) for x in i5_p150[0]]
+y = [x[0] for x in i5_p150[1]]
+axs[1].bar(x, y, color='#009440')
+x = np.arange(len(y))
+fittedParameters, pcov = curve_fit(func, x, y)
+y_fit = func(x, *fittedParameters)
+axs[1].plot(x, y_fit, 'k:')
+
+axs[2].set_title('2 initial fishes')
+# axs[2].set_ylabel('Herding Rate')
+axs[2].set_xlabel('Initial shark survival time t * 100')
[…]

### 2021-01-09 paper/paper.tex
Add a bunch of analysis/explanations to most figures.

@@
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=8cm]{figures/dqncomp1fish_2.png}
-\caption{Sustainability of static, static-wait, DQN Stage II and PPO with initial fish population of 1.}
-\label{fig:dqncomp1}
-\end{center}
-\end{figure}
+TODO: Define sustainability
 
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=8cm]{figures/dqncomp2fish_2.png}
-\caption{Sustainability of static, static-wait, DQN Stage II and PPO with initial fish population of 2.}
-\label{fig:dqncomp2}
-\end{center}
-\end{figure}
+\begin{figure*}%
+    \centering
+    \subfloat[][\centering Sustainability with 1 initial fish.]{\includegraphics[width=7.5cm]{figures/dqncomp1fish_2.png} }%
+    \subfloat[][\centering Sustainability with 2 initial fishes.]{\includegraphics[width=7.5cm]{figures/dqncomp2fish_2.png} }%
+    \caption{Sustainability of static, static-wait, DQN Stage II and PPO.
+PPO consistently leads to the most sustainable behavior due to herding a rather large fish population, which results in a higher rate of fish procreations and thus more prey to be caught.
+20 models were trained for each DQN Stage II and PPO for each scenario.}
+    \label{fig:dqncomp}%
+\end{figure*}
 
@@
 \includegraphics[width=8cm]{figures/fish_pop_chart3.png}
-\caption{Left-over fish population per learning episode over 12M steps.}
+    \caption{Left-over fish population per learning episode over 12M steps.
+In this setting there is at maximum 6 fishes in the population.
+When sharks learn to herd fishes, they go through 3 stages.
+Stage $a$, in which they cannot hunt effectively yet and thus leave the full population intact at the end of the episode.
+Stage $b$, in which they effectively hunt and overhunt, leaving no fishes at the end of the epsiode.
+Lastly, stage $c$, in which they learn to keep a herd of 2 fishes around, up until the end of the epsiode.}
 \label{fig:fish_pop}
@@
 \includegraphics[width=6cm]{figures/shark_speeds.png}
-\caption{Distribution of shark speeds over time.}
+\caption{From back to front: Distribution of shark speeds over time.
+When sharks learn to herd fishes, the distribution of their speed becomes bimodal after a while --- suggesting that sometimes they wait while other times they actively hunt at high speed.}
 \label{fig:shark_speeds}
@@
 
+TODO: Define active herding.
+
 \begin{figure*}[t]
 \begin{center}
-\includegraphics[width=\textwidth]{figures/herding.png}
-\caption{TODO}
+\includegraphics[width=.9\textwidth]{figures/herding.png}
+    \caption{Herding rate in different scenarios.
+From left to right, initial fish population is decreased (10, 5, 2).
+A lower fish population increases sustainability pressure --- the sharks get into the situation of 0 left fishes much quicker.
+Further, each scenario varies the initial shark survival time.
+Especially in the scenario with just two fishes the importance of this parameter becomes clear --- giving the sharks an initial 1200 steps induces the highest rate of herding.
+While low initial survival steps induce too much survival pressure, thus overriding any sustainability with the need for survival, too high initial survival steps do not induce enough pressure, reducing the need for active herding as the sharks now often do not actively hunt but just idle.
+The curve was fitted using 4 polynomials and each bar represents 20 models.}
 \label{fig:herding}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figures/coop_movie_frames2.png}
+\includegraphics[width=.9\textwidth]{figures/coop_movie_frames2.png}
 \caption{From left to right: Two sharks cooperatively catch a fish.}
@@
     \subfloat[][\centering Cooperation rate with initial fish population of 5 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
-    \caption{Cooperation rate in different scenarios.}%
+    \caption{Cooperation rate in different scenarios. TODO: Analysis}%
     \label{fig:coop}%
@@
 \includegraphics[width=14cm]{figures/coop_vs_sterberisiko_5fish.png}
-\caption{Cooperation rate vs starving pressure with initial fish population of 5.}
+\caption{Cooperation rate vs starving pressure with initial fish population of 5. TODO: Analysis}
 \label{fig:coop_starve}

### 2021-01-09 visualize_herding.py

@@ -12,6 +12,8 @@ with open(base_path + 'i5_p150_two_net_herding.pickle', 'rb') as f:
     i5_p150 = pickle.load(f)
 with open(base_path + 'i5_p75_two_net_herding.pickle', 'rb') as f:
     i5_p75 = pickle.load(f)
+with open(base_path + 'i2_p150_sp500_two_net_herding.pickle', 'rb') as f:
+    i2_p150 = pickle.load(f)
 
 
 print(i10_p150)

### 2021-01-09 visualize_coop_starve.py
Extend coop chart to four subcharts

@@ -55,6 +55,8 @@ with open(base_path + 'i5_coop_starve.pickle', 'rb') as f:
     i5_data2, i5_label_data2 = _prep(pickle.load(f), prefix='t1500_i5')
 with open(base_path + 'i5_coop_starve.pickle', 'rb') as f:
     i5_data3, i5_label_data3 = _prep(pickle.load(f), prefix='t1000_i5')
+with open(base_path + 't500_i5_coop_starve.pickle', 'rb') as f:
+    i5_data4, i5_label_data4 = _prep(pickle.load(f), prefix='t500_i5')
 
 with open(base_path + 'i10_coop_starve.pickle', 'rb') as f:
     i10_data, i10_label_data = _prep(pickle.load(f), prefix='t2000_i10')
@@ -62,22 +64,25 @@ with open(base_path + 'i10_coop_starve.pickle', 'rb') as f:
     i10_data2, i10_label_data2 = _prep(pickle.load(f), prefix='t1500_i10')
 with open(base_path + 'i10_coop_starve.pickle', 'rb') as f:
     i10_data3, i10_label_data3 = _prep(pickle.load(f), prefix='t1000_i10')
+with open(base_path + 't500_i10_coop_starve.pickle', 'rb') as f:
+    i10_data4, i10_label_data4 = _prep(pickle.load(f), prefix='t500_i10')
 
 
-def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_data3):
+def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_data3, i5_data4, i5_label_data4):
     print(i5_data)
 
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.04', '.05']
 
     cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
-    fig, (ax, ax2, ax3) = plt.subplots(1, 3, figsize=(6.5, 2.0), constrained_layout=True)
-    im = ax.imshow(i5_data, cmap=cmap_mod)
-    im2 = ax2.imshow(i5_data2, cmap=cmap_mod)
-    im3 = ax3.imshow(i5_data3, cmap=cmap_mod)
+    fig, (ax, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=(8.5, 2.0), constrained_layout=True)
[…]

### 2021-01-09 env/aquarium.pyx
Add self.steps_til_first_kill

@@ -142,6 +142,7 @@ class Aquarium:
         self.coop_kills = 0
         self.full_coop_kills = 0
         self.n_stuns = 0
+        self.steps_til_first_kill = 0
 
         # Kill zone
         self.shared_kill_zone = shared_kill_zone
@@ -378,6 +379,8 @@ class Aquarium:
     def _on_shark_fish_collision(self, shark, fish):
         if fish in self.fishes:
             self.fishes.remove(fish)
+        if self.steps_til_first_kill == 0:
+            self.steps_til_first_kill = self.current_step
         if shark in self.track_shark_reward:
             # This was to check whether we have real cooperation or
             # herding.
@@ -412,7 +415,7 @@ class Aquarium:
                 n_participating_sharks = len(participating_sharks)
                 if n_participating_sharks > 0:
                     self.coop_kills += 1
-                if n_participating_sharks == len(self.sharks) - 1:
+                if n_participating_sharks >= len(self.sharks) - 1:
                     self.full_coop_kills += 1
 
                 reward_main_shark = 10. 

### 2021-01-09 paper/paper.tex
Minor changes to paper

@@
 \title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
-\author{Fabian Ritz Ratke$^{1}$, Daniel Ratke$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
+\author{Fabian Ritz$^{1}$, Daniel Ratke$^{2}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
 \mbox{}\\
@@
     \centering
-    \subfloat[][\centering Cooperation rate with initial fish population of 10.]{\includegraphics[width=5.5cm]{figures/coop_chart_split1.png} }%
-    \subfloat[][\centering Cooperation rate with initial fish population of 5.]{\includegraphics[width=5.5cm]{figures/coop_chart_split2.png} }%
-    \subfloat[][\centering Cooperation rate with initial fish population of 5 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
+    \subfloat[][\centering Cooperation rate with initial fish population of 5.]{\includegraphics[width=5.5cm]{figures/coop_chart_split1.png} }%
+    \subfloat[][\centering Cooperation rate with initial fish population of 10.]{\includegraphics[width=5.5cm]{figures/coop_chart_split2.png} }%
+    \subfloat[][\centering Cooperation rate with initial fish population of 10 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
     \caption{Cooperation rate in different scenarios. TODO: Analysis}%

### 2021-01-09 evaluator_herding.py
Add i2 support to evaluator_herding

@@ -126,6 +126,20 @@ def main(id_):
         't2000': 'ma3_obs_starve_maxsteps_t2000_i2_p150'
     }
 
+    cfg_ids_i2_p150_AAA = {
+        't200': 'ma3_obs_starve_maxsteps_t200_i2_p150_sp500',
+        't300': 'ma3_obs_starve_maxsteps_t300_i2_p150_sp500',
+        't400': 'ma3_obs_starve_maxsteps_t400_i2_p150_sp500',
+        't500': 'ma3_obs_starve_maxsteps_t500_i2_p150_sp500',
+        't600': 'ma3_obs_starve_maxsteps_t600_i2_p150_sp500',
+        't700': 'ma3_obs_starve_maxsteps_t700_i2_p150_sp500',
+        't800': 'ma3_obs_starve_maxsteps_t800_i2_p150_sp500',
+        't1000': 'ma3_obs_starve_maxsteps_t1000_i2_p150_sp500',
+        't1200': 'ma3_obs_starve_maxsteps_t1200_i2_p150_sp500',
+        't1500': 'ma3_obs_starve_maxsteps_t1500_i2_p150_sp500',
+        't2000': 'ma3_obs_starve_maxsteps_t2000_i2_p150_sp500'
+    }
+
     two_net = True
 
     kv = None
@@ -139,6 +153,8 @@ def main(id_):
         kv = cfg_ids_i5_p150
     elif id_ == 'i2_p150':
         kv = cfg_ids_i2_p150
+    elif id_ == 'i2_p150_AAA':
+        kv = cfg_ids_i2_p150_AAA
 
     # What the fuck. Pool doesn't work.
     # Didn't have the time to investigate so I went for the hacky solution.

### 2021-01-09 evaluator_coop_starve.py
Add evaluator_herding_sp100

@@ -29,21 +29,22 @@ def load(id_, cfg_id, base_cfg_id, return_dict):
     coop_ratios = []
     for fname in res:
         fname = fname[:-3]
-        print(fname)
+        # print(fname)
         for _ in range(20):
             exp = Experiment(base_cfg_id, show_gui=False, dump_cfg=False)
             exp.load_eval(fname, steps=3000, initial_survival_time=3000)
             if exp.env.dead_fishes != 0:
+                print(exp.env.coop_kills, exp.env.dead_fishes)
                 coop_ratios.append(exp.env.coop_kills / exp.env.dead_fishes)
             else:
-                print('####################')
-                print('NO dead fishes!')
-                print('####################')
-            # TODO DUBIOUS! Should we maybe add a [0] if there's no dead fishes?
+                print('####### NO dead fishes! #######')
+                # TODO DUBIOUS! Should we maybe add a [0] if there's no dead fishes?
+                # lets try.
+                coop_ratios.append(0)
 
     if coop_ratios:
         ci = st.t.interval(0.95, len(coop_ratios)-1, loc=np.mean(coop_ratios), scale=st.sem(coop_ratios))
-        print('avg_coop_ratio:%d' % np.mean(coop_ratios))
+        print('avg_coop_ratio:%d' % np.mean(coop_ratios), coop_ratios)
         return_dict[id_] = (np.mean(coop_ratios), ci)
     else:
         return_dict[id_] = (0, (0, 0))
@@ -81,12 +82,22 @@ def main(id_):
         't1000_i5_r6_s05': ['ma9_t1000_i5_p150_r6_s05_stun_ext', 'ma9_t3000_i5_p150_r6_s05_stun_ext'],
[…]

### 2021-01-09 evaluator_herding_sp100.py

@@ -1,0 +1,155 @@
+import sys
+import glob
+import pickle
+import multiprocessing
+from multiprocessing import Process
+from collections import OrderedDict
+from pipeline import Experiment
+
+
+def load(id_, cfg_id, return_dict):
+    # base_cfg_id = 'ma3_obs'  # for i10, i5 (sp600)
+    # base_cfg_id = 'ma3_obs_sp100'  # for i2
+    base_cfg_id = 'ma3_obs'
+    base_paths = ['models']
+    res = []
+    two_net = 'two_net' in cfg_id
+    for base_path in base_paths:
+        id__ = base_path + "/%s-*-F"
+        if two_net:
+            id__ = base_path + "/%s-*-F-m1"
+        res.extend(list(glob.glob(id__ % cfg_id)))
+    # print(res)
+    counter_coop = 0.
+    counter_fail = 0.
+    counter_greedy = 0.
+    for fname in res:
+        if two_net:
+            fname = fname[:-3]
+        print('#############################')
+        print(fname)
+        for _ in range(3):
+            exp = Experiment(base_cfg_id, show_gui=False, dump_cfg=False)
+            fish_pop_hist, _ = exp.load_eval(fname, steps=5000)
+            if fish_pop_hist[-1] > 0 and fish_pop_hist[-1] < 10:
+                counter_coop += 1
+            if fish_pop_hist[-1] == 0:
+                counter_greedy += 1
+            if fish_pop_hist[-1] >= 10:
+                counter_fail += 1
+
+            # TODO: For i2 !
+            # if fish_pop_hist[-1] > 0 and exp.env.dead_fishes > 0:
+            #     counter_coop += 1
+            # print(exp.env.dead_fishes)
+
+        total = counter_coop + counter_greedy + counter_fail
+        print('c:%d' %counter_coop, 'f:%d' % counter_fail, 'g:%d' % counter_greedy, 't:%d' % total)
+
+    print('coop', counter_coop / total)
+    print('greedy', counter_greedy / total)
+    print('fail', counter_fail / total)
+    return_dict[id_] = (counter_coop / total, total)
+    # return id_, (counter_coop / total, total)
+
+
+def main(id_):
[…]

### 2021-01-10 plots/gen_herding_distr_plot.py
Add lots of new (alternative) herding pickles and adapt the respective plot generator.

@@ -11,12 +11,29 @@ plt.rc('font', family='Raleway')
 
 base_path = '../pickles/'
 
-with open(base_path + 'i10_p150_two_net_herding.pickle', 'rb') as f:
-    i10_p150 = pickle.load(f)
-with open(base_path + 'i5_p150_two_net_herding.pickle', 'rb') as f:
-    i5_p150 = pickle.load(f)
-with open(base_path + 'i2_p150_sp500_two_net_herding.pickle', 'rb') as f:
-    i2_p150 = pickle.load(f)
+sp100_ma3obs = False
+sp100_ma3obs_sp100 = False
+if sp100_ma3obs:
+    with open(base_path + 'i10_two_net_herding_sp100_ma3obs.pickle', 'rb') as f:
+        i10_p150 = pickle.load(f)
+    with open(base_path + 'i5_two_net_herding_sp100_ma3obs.pickle', 'rb') as f:
+        i5_p150 = pickle.load(f)
+    with open(base_path + 'i2_two_net_herding_sp100_ma3obs.pickle', 'rb') as f:
+        i2_p150 = pickle.load(f)
+elif sp100_ma3obs_sp100:
+    with open(base_path + 'i10_two_net_herding_sp100.pickle', 'rb') as f:
+        i10_p150 = pickle.load(f)
+    with open(base_path + 'i5_two_net_herding_sp100.pickle', 'rb') as f:
+        i5_p150 = pickle.load(f)
+    with open(base_path + 'i2_two_net_herding_sp100.pickle', 'rb') as f:
+        i2_p150 = pickle.load(f)
+else:
+    with open(base_path + 'i10_p150_two_net_herding.pickle', 'rb') as f:
+        i10_p150 = pickle.load(f)
+    with open(base_path + 'i5_p150_two_net_herding.pickle', 'rb') as f:
+        i5_p150 = pickle.load(f)
+    with open(base_path + 'i2_p150_sp500_two_net_herding.pickle', 'rb') as f:
+        i2_p150 = pickle.load(f)
 
 
 print(i10_p150)
@@ -69,3 +86,4 @@ axs[2].plot(x, y_fit, 'k:')
 plt.tight_layout()
 plt.ylim(0., 1.0)
 plt.show()
+fig.savefig("herding.pdf", bbox_inches='tight')

### 2021-01-10 visualize_herding_old.py
Rename visualize_herding.py -> visualize_herding_old.py

@@ -53,3 +53,4 @@ fig.text(.02, .04, txt, wrap=True)
 # fig.set_size_inches(11, 6, forward=True)
 plt.subplots_adjust(left=0.05, right=0.95, top=0.9, bottom=0.2)
 plt.show()
+fig.savefig("plots/herding.pdf", bbox_inches='tight')

### 2021-01-10 plots/gen_dqn_comp_chart2.py
Add pdf versions of a few figures.

@@ -93,7 +93,7 @@ def bar_plot(
         ax.legend(bars, data.keys())
 
 
-def plot(data, err_data, data2, err_data2):
+def plot(data, err_data, data2, err_data2, xxx=22):
     scenarios = [100, 200, 300]
     fig, ax = plt.subplots(figsize=(4, 3.5))
     bar_plot(
@@ -111,7 +111,7 @@ def plot(data, err_data, data2, err_data2):
     arr_img = plt.imread(fn, format='png')
     imagebox = OffsetImage(arr_img, zoom=0.07)
     imagebox.image.axes = ax
-    xy = [0.3, 22]
+    xy = [0.3, xxx]
     ab = AnnotationBbox(imagebox, xy,
                         xybox=(50., 0.),
                         xycoords='data',
@@ -153,6 +153,7 @@ def plot(data, err_data, data2, err_data2):
     plt.xlim(-0.5, 2.5)
     plt.tight_layout()
     plt.show()
+    return fig
 
 
 if __name__ == "__main__":
@@ -181,7 +182,8 @@ if __name__ == "__main__":
         "DQN Stage II": [0.149947, 0.013550, 0.014765],
         "PPO": [0.130000, 0.080000, 0.070000]
     }
-    plot(data, err_data, data2, err_data2)
+    fig = plot(data, err_data, data2, err_data2, xxx=20)
+    fig.savefig("dqncomp1.pdf", bbox_inches='tight')
 
     # 2 fish
     data = {
@@ -208,4 +210,5 @@ if __name__ == "__main__":
         "DQN Stage II": [0.252410, 0.025981, 0.024373],
         "PPO": [0.060000, 0.110000, 0.070000]
     }
-    plot(data, err_data, data2, err_data2)
+    fig = plot(data, err_data, data2, err_data2)
+    fig.savefig("dqncomp2.pdf", bbox_inches='tight')

### 2021-01-10 plots/gen_inn_last_fish_pop_chart.py

@@ -21,7 +21,7 @@ def moving_average(x, w):
 a = moving_average(a, 100)
 print(len(a))
 
-plt.figure(figsize=(4, 3))
+fig = plt.figure(figsize=(4, 3))
 plt.plot(a, linewidth=.8, c='#ffffff')
 plt.ylabel('Fish population at the end of an episode')
 plt.xlabel('Steps in million')
@@ -37,3 +37,4 @@ plt.xlim(0, 13980)
 plt.ylim(0, 7)
 plt.tight_layout()
 plt.show()
+fig.savefig("last_fish_pop.pdf", bbox_inches='tight')

### 2021-01-10 plots/gen_coop_chart.py
Add pdf versions for coop charts too.

@@ -54,8 +54,8 @@ def _prep(data, prefix='i10'):
     return data, label_data
 
 
-base_path = 'pickles/'
-stuns = True
+base_path = '../pickles/'
+stuns = False
 if stuns:
     with open(base_path + 'i10_stun_coop.pickle', 'rb') as f:
         i10_data, i10_label_data = _prep(pickle.load(f))
@@ -100,6 +100,7 @@ def plot(data, label_data):
     # ax.set_title("Fish population: 10")
     # ax2.set_title("Fish population: 5")
     plt.show()
+    return fig
 
 
 def plot_both():
@@ -139,7 +140,16 @@ def plot_both():
     # ax.set_title("Fish population: 10")
     # ax2.set_title("Fish population: 5")
     plt.show()
+    return fig
 
 
-plot(i5_data, i5_label_data)
-plot(i10_data, i10_label_data)
+fig = plot(i5_data, i5_label_data)
+if stuns:
+    fig.savefig("i5_coop_stuns.pdf", bbox_inches='tight')
+else:
+    fig.savefig("i5_coop.pdf", bbox_inches='tight')
+fig = plot(i10_data, i10_label_data)
+if stuns:
+    fig.savefig("i10_coop_stuns.pdf", bbox_inches='tight')
+else:
+    fig.savefig("i10_coop.pdf", bbox_inches='tight')

### 2021-01-10 plots/gen_coop_starve_chart.py

@@ -48,14 +48,16 @@ def _prep(data, prefix='i10'):
     return data, label_data
 
 
-base_path = 'pickles/'
+base_path = '../pickles/'
 with open(base_path + 'i5_coop_starve.pickle', 'rb') as f:
     i5_data, i5_label_data = _prep(pickle.load(f), prefix='t2000_i5')
 with open(base_path + 'i5_coop_starve.pickle', 'rb') as f:
     i5_data2, i5_label_data2 = _prep(pickle.load(f), prefix='t1500_i5')
 with open(base_path + 'i5_coop_starve.pickle', 'rb') as f:
     i5_data3, i5_label_data3 = _prep(pickle.load(f), prefix='t1000_i5')
-with open(base_path + 't500_i5_coop_starve.pickle', 'rb') as f:
+# with open(base_path + 't500_i5_coop_starve.pickle', 'rb') as f:
+#     i5_data4, i5_label_data4 = _prep(pickle.load(f), prefix='t500_i5')
+with open(base_path + 'i5_coop_starve.pickle', 'rb') as f:
     i5_data4, i5_label_data4 = _prep(pickle.load(f), prefix='t500_i5')
 
 with open(base_path + 'i10_coop_starve.pickle', 'rb') as f:
@@ -76,10 +78,10 @@ def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_da
 
     cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
     fig, (ax, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=(8.5, 2.0), constrained_layout=True)
-    im = ax.imshow(i5_data4, cmap=cmap_mod)
-    im2 = ax2.imshow(i5_data, cmap=cmap_mod)
-    im3 = ax3.imshow(i5_data2, cmap=cmap_mod)
-    im4 = ax4.imshow(i5_data3, cmap=cmap_mod)
+    im = ax.imshow(i5_data4, cmap=cmap_mod, vmin=0, vmax=1)
+    im2 = ax2.imshow(i5_data, cmap=cmap_mod, vmin=0, vmax=1)
+    im3 = ax3.imshow(i5_data2, cmap=cmap_mod, vmin=0, vmax=1)
+    im4 = ax4.imshow(i5_data3, cmap=cmap_mod, vmin=0, vmax=1)
 
     # Colorbar
     cbar = ax.figure.colorbar(im, ax=[ax, ax2, ax3, ax4], aspect=40)
[…]

### 2021-01-10 plots/gen_coop_starve_chart.py
Update coop charts (dimensions)

@@ -34,6 +34,9 @@ def _prep(data, prefix='i10'):
         ret_labels[k] = '%0.2f\n±%0.2f' % (round(mean, 2), round(ci, 2))
     print(ret_labels)
 
+    print('##', prefix)
+    print(ret)
+
     data = [
         [ret[prefix + '_r4_s03'], ret[prefix + '_r4_s04'], ret[prefix + '_r4_s05']],
         [ret[prefix + '_r6_s03'], ret[prefix + '_r6_s04'], ret[prefix + '_r6_s05']],

### 2021-04-30 plots/gen_coop_chart.py
Re-generate some of the matrix plots with new colors, fix font sizes.

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -58,7 +59,7 @@ def plot(data, label_data, do_cbar=False):
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
     fig, ax = plt.subplots(1, 1, figsize=(3.5, 2.0), constrained_layout=True)
     im = ax.imshow(data, cmap=cmap_mod, vmin=0.0, vmax=1.0)
 
@@ -73,12 +74,15 @@ def plot(data, label_data, do_cbar=False):
     ax.set_xticklabels(x_labels)
     ax.set_yticklabels(y_labels)
     ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=10)
 
     # Text annotations
     for i in range(len(y_labels)):
         for j in range(len(x_labels)):
-            ax.text(j, i, label_data[i][j], ha="center", va="center", color="w")
+            col = 'w'
+            if data[i][j] < .55:
+                col = 'black'
+            ax.text(j, i, label_data[i][j], ha="center", va="center", color=col)
 
     # ax.set_title("Fish population: 10")
     # ax2.set_title("Fish population: 5")
@@ -92,7 +96,7 @@ def plot_both():
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
     fig, (ax, ax2) = plt.subplots(1, 2, figsize=(6, 2.0), constrained_layout=True)
     im = ax.imshow(i10_data, cmap=cmap_mod)
     im2 = ax2.imshow(i5_data, cmap=cmap_mod)

### 2021-04-30 plots/gen_coop_net3_chart.py

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -98,7 +99,7 @@ def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_da
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
     fig, (ax, ax2, ax3, ax4, ax5) = plt.subplots(1, 5, figsize=(14.5, 2.0), constrained_layout=True)
     im = ax.imshow(i5_data, cmap=cmap_mod, vmin=0, vmax=1)
     im2 = ax2.imshow(i5_data2, cmap=cmap_mod, vmin=0, vmax=1)
@@ -160,7 +161,7 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
 
     data = [i5_data3]
     label_data = [i5_label_data3]
@@ -187,13 +188,17 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_yticks(np.arange(len(y_labels)))
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+        if m <= 1:
+            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations
         for i in range(len(y_labels)):
             for j in range(len(x_labels)):
-                ax.text(j, i, ld[i][j], ha="center", va="center", color="w")
[…]

### 2021-04-30 plots/gen_coop_net3_dead_fishes_chart.py

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -133,7 +134,7 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
     # x_labels = ['.025', '.03', '.035', '.04', '.05']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
 
     data = [i5_data3, i5_data4]
     label_data = [i5_label_data3, i5_label_data4]
@@ -160,13 +161,17 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_yticks(np.arange(len(y_labels)))
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+        if m == 0:
+            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations
         for i in range(len(y_labels)):
             for j in range(len(x_labels)):
-                ax.text(j, i, ld[i][j+1], ha="center", va="center", color="w")
+                col = 'w'
+                if d[i][j] < .55:
+                    col = 'black'
+                ax.text(j, i, ld[i][j+1], ha="center", va="center", color=col)
 
         print(id_ + "_coop_net3_dead_" + str(m) + ".pdf")
         fig.savefig(id_ + "_coop_net3_dead_" + str(m) + ".pdf", bbox_inches='tight')

### 2021-04-30 plots/gen_coop_shared_net3_chart.py

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -151,7 +152,7 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2):
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
 
     data = [i5_data, i5_data2]
     label_data = [i5_label_data, i5_label_data2]
@@ -172,13 +173,16 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2):
         ax.set_yticks(np.arange(len(y_labels)))
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations
         for i in range(len(y_labels)):
             for j in range(len(x_labels)):
-                ax.text(j, i, ld[i][j], ha="center", va="center", color="w")
+                col = 'w'
+                if d[i][j] < .55:
+                    col = 'black'
+                ax.text(j, i, ld[i][j], ha="center", va="center", color=col)
 
         print(id_ + "_coop_net3_shared" + str(m) + ".pdf")
         fig.savefig(id_ + "_coop_net3_shared" + str(m) + ".pdf", bbox_inches='tight')

### 2021-04-30 plots/gen_coop_starve_chart.py

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -101,7 +102,7 @@ def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_da
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
     fig, (ax, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=(8.5, 2.0), constrained_layout=True)
     im = ax.imshow(i5_data4, cmap=cmap_mod, vmin=0, vmax=1)
     im2 = ax2.imshow(i5_data, cmap=cmap_mod, vmin=0, vmax=1)
@@ -154,7 +155,7 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.4, maxval=.99)
 
     data = [i5_data4, i5_data, i5_data2, i5_data3]
     label_data = [i5_label_data4, i5_label_data, i5_label_data2, i5_label_data3]
@@ -176,12 +177,15 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
         ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=10)
 
         # Text annotations
         for i in range(len(y_labels)):
             for j in range(len(x_labels)):
-                ax.text(j, i, ld[i][j], ha="center", va="center", color="w")
+                col = 'w'
+                if d[i][j] < .55:
+                    col = 'black'
[…]

### 2021-04-30 plots/gen_coop_starve_failure_chart.py

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -86,7 +87,7 @@ def doit(i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3, i5_label_da
 
     data_max = np.max([i5_data, i5_data2, i5_data3, i5_data4])
 
-    cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
     fig, (ax, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=(8.5, 2.0), constrained_layout=True)
     im = ax.imshow(i5_data4, cmap=cmap_mod, vmin=0, vmax=data_max)
     im2 = ax2.imshow(i5_data, cmap=cmap_mod, vmin=0, vmax=data_max)
@@ -140,7 +141,7 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
     x_labels = ['.03', '.04', '.05']
 
     # cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
-    cmap_mod = truncate_colormap('Blues', minval=.5, maxval=.99)
+    # cmap_mod = truncate_colormap('Blues', minval=.5, maxval=.99)
 
     data = [i5_data4, i5_data, i5_data2, i5_data3]
     label_data = [i5_label_data4, i5_label_data, i5_label_data2, i5_label_data3]
@@ -162,12 +163,15 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
         ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=10)
 
         # Text annotations
         for i in range(len(y_labels)):
             for j in range(len(x_labels)):
-                ax.text(j, i, ld[i][j], ha="center", va="center", color="w")
+                col = 'w'
+                if d[i][j] < .55:
+                    col = 'black'
[…]

### 2021-04-30 plots/gen_coop_vd20_chart.py

@@ -4,6 +4,7 @@ import matplotlib
 import matplotlib.pyplot as plt
 import matplotlib.colors as colors
 import matplotlib as mpl
+from lib import cmap_mod
 
 
 mpl.font_manager._rebuild()
@@ -58,7 +59,7 @@ def plot(data, label_data, do_cbar=False):
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
     fig, ax = plt.subplots(1, 1, figsize=(3.5, 2.0), constrained_layout=True)
     im = ax.imshow(data, cmap=cmap_mod, vmin=0.0, vmax=1.0)
 
@@ -72,13 +73,17 @@ def plot(data, label_data, do_cbar=False):
     ax.set_yticks(np.arange(len(y_labels)))
     ax.set_xticklabels(x_labels)
     ax.set_yticklabels(y_labels)
-    ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=9)
+    if not do_cbar:
+        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
     # Text annotations
     for i in range(len(y_labels)):
         for j in range(len(x_labels)):
-            ax.text(j, i, label_data[i][j], ha="center", va="center", color="w")
+            col = 'w'
+            if data[i][j] < .55:
+                col = 'black'
+            ax.text(j, i, label_data[i][j], ha="center", va="center", color=col)
 
     # ax.set_title("Fish population: 10")
     # ax2.set_title("Fish population: 5")
@@ -92,7 +97,7 @@ def plot_both():
     y_labels = ['4', '6', '10']
     x_labels = ['.03', '.035', '.04', '.05']
 
-    cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
+    # cmap_mod = truncate_colormap('Greens', minval=.3, maxval=.99)
[…]

### 2021-04-30 plots/lib.py

@@ -1,0 +1,39 @@
+import seaborn as sns
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+from matplotlib.colors import ListedColormap
+
+
+def truncate_colormap(cmapIn='jet', minval=0.0, maxval=1.0, n=100):
+    cmapIn = plt.get_cmap(cmapIn)
+
+    new_cmap = colors.LinearSegmentedColormap.from_list(
+        'trunc({n},{a:.2f},{b:.2f})'.format(n=cmapIn.name, a=minval, b=maxval),
+        cmapIn(np.linspace(minval, maxval, n)))
+
+    return new_cmap
+
+
+def truncate_colormap2(cmapIn, minval=0.0, maxval=1.0, n=100):
+    return colors.LinearSegmentedColormap.from_list(
+        'trunc({n},{a:.2f},{b:.2f})'.format(n=cmapIn.name, a=minval, b=maxval),
+        cmapIn(np.linspace(minval, maxval, n)))
+
+
+# cmap_mod = truncate_colormap('viridis_r', minval=.4, maxval=.99)
+# cmap_mod = truncate_colormap('summer_r', minval=.4, maxval=.99)
+# cmap_mod = truncate_colormap('summer_r', minval=.0, maxval=.99)
+# cmap_mod = truncate_colormap('bone_r', minval=.0, maxval=.99)
+# cmap_mod = sns.light_palette("mako", as_cmap=True)
+
+# cmap_mod = sns.color_palette("mako", as_cmap=True).reversed()
+# cmap_mod = truncate_colormap2(cmap_mod, minval=.0, maxval=.8)
+cmap_mod = sns.color_palette("mako", as_cmap=True).reversed()
+cmap_mod = truncate_colormap2(cmap_mod, minval=-.2, maxval=.9)
+# cmap_mod = truncate_colormap2(cmap_mod, minval=-.0, maxval=.9)  # Used for failure chart
+
+# n = cmap_mod.N
+# cmap_mod = cmap_mod(np.arange(cmap_mod.N))
+# cmap_mod[:, -1] = .95  # np.linspace(0, 1, n)
+# cmap_mod = ListedColormap(cmap_mod)

### 2021-05-01 plots/gen_coop_chart.py
Update all plots (font sizes, colors).

@@ -73,8 +73,9 @@ def plot(data, label_data, do_cbar=False):
     ax.set_yticks(np.arange(len(y_labels)))
     ax.set_xticklabels(x_labels)
     ax.set_yticklabels(y_labels)
-    ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=10)
+    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
+    ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10.8, loc="bottom")
+    ax.yaxis.set_label_coords(-.14, -.26)
 
     # Text annotations
     for i in range(len(y_labels)):

### 2021-05-01 plots/gen_coop_net3_chart.py

@@ -189,7 +189,8 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
         if m <= 1:
-            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=11, loc="bottom")
+            ax.yaxis.set_label_coords(-.14, -.22)
         ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations

### 2021-05-01 plots/gen_coop_net3_dead_fishes_chart.py

@@ -162,7 +162,8 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
         if m == 0:
-            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=11, loc="bottom")
+            ax.yaxis.set_label_coords(-.14, -.22)
         ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations

### 2021-05-01 plots/gen_coop_shared_net3_chart.py

@@ -173,7 +173,8 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2):
         ax.set_yticks(np.arange(len(y_labels)))
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
+        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=11, loc="bottom")
+        ax.yaxis.set_label_coords(-.14, -.22)
         ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations

### 2021-05-01 plots/gen_coop_starve_chart.py

@@ -176,8 +176,10 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_yticks(np.arange(len(y_labels)))
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=10)
+        if m <= 1:
+            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=11, loc="bottom")
+            ax.yaxis.set_label_coords(-.17, -.23)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations
         for i in range(len(y_labels)):

### 2021-05-01 plots/gen_coop_starve_failure_chart.py

@@ -162,8 +162,10 @@ def doit_single(id_, i5_data, i5_label_data, i5_data2, i5_label_data2, i5_data3,
         ax.set_yticks(np.arange(len(y_labels)))
         ax.set_xticklabels(x_labels)
         ax.set_yticklabels(y_labels)
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=9)
-        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=10)
+        if m <= 1:
+            ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=11, loc="bottom")
+            ax.yaxis.set_label_coords(-.17, -.23)
+        ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
 
         # Text annotations
         for i in range(len(y_labels)):

### 2021-05-01 plots/gen_coop_vd20_chart.py

@@ -74,8 +74,9 @@ def plot(data, label_data, do_cbar=False):
     ax.set_xticklabels(x_labels)
     ax.set_yticklabels(y_labels)
     if not do_cbar:
-        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=10)
-    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=11)
+        ax.set_ylabel('Shared Catch Zone Radius', rotation=90, va="bottom", fontsize=11, loc="bottom")
+        ax.yaxis.set_label_coords(-.14, -.22)
+    ax.set_xlabel('Predator Speed', rotation=0, va="top", fontsize=12)
 
     # Text annotations
     for i in range(len(y_labels)):

### 2021-05-01 plots/gen_dqn_comp_chart2.py

@@ -114,15 +114,19 @@ def bar_plot(
         err = err_data[name]
         err2 = err_data2[name]
         values2 = data2[name]
+        hatch = None
+        if 'Static' in name:
+            hatch = '//'
         for x, y in enumerate(values):
             bar = ax.bar(
                 x + x_offset, y, yerr=err[x], width=bar_width * single_width,
-                color=colors[i % len(colors)], edgecolor='black', linewidth=.3
+                color=colors[i % len(colors)], edgecolor='black', linewidth=.3,
+                hatch=hatch
             )
             bar = ax.bar(
                 x + x_offset, values2[x], yerr=err2[x], width=bar_width *
                 single_width, color=colors[i % len(colors)], edgecolor='black',
-                linewidth=.3, bottom=y+.15
+                linewidth=.3, bottom=y+.15, hatch=hatch
             )
 
         # Add a handle to the last drawn bar, which we'll need for the legend
@@ -197,8 +201,8 @@ def plot(data, err_data, data2, err_data2, xxx=22):
     ax.legend([*bars, p1, p2], [*data_keys, 'Prey caught', 'Left-over prey'], handler_map={p1: custom_handler1, p2: custom_handler2})
 
     plt.xticks([0, 1, 2], scenarios)
-    plt.xlabel('Time until reproduction possible')
-    plt.ylabel(r'Sustainability $\sigma$')
+    plt.xlabel('Time until reproduction possible', fontsize=11)
+    plt.ylabel(r'Sustainability $\sigma$', fontsize=11)
     plt.xlim(-0.5, 2.5)
     plt.tight_layout()
     plt.show()

### 2021-05-01 plots/gen_herding_distr_plot.py

@@ -3,6 +3,7 @@ import matplotlib.pyplot as plt
 import matplotlib as mpl
 import numpy as np
 from scipy.optimize import curve_fit
+from lib import col1
 
 
 mpl.font_manager._rebuild()
@@ -51,11 +52,12 @@ def func(x, a, b, c, d, e):
 fig, axs = plt.subplots(1, 3, figsize=(9, 3), sharey=True)
 
 axs[0].set_title('10 initial prey')
-axs[0].set_ylabel(r'Herding Ratio $\eta$')
-axs[0].set_xlabel(r'Initial predator survival time t $\times$ 100')
+axs[0].set_ylabel(r'Herding Ratio $\eta$', fontsize=11)
+axs[0].set_xlabel(r'Initial predator survival time t $\times$ 100', fontsize=11)
 x = [str(int(x[1:]) // 100) for x in i10_p150[0]]
 y = [x[0] for x in i10_p150[1]]
-axs[0].bar(x, y, color='#009440')
+# axs[0].bar(x, y, color='#009440')
+axs[0].bar(x, y, color=col1)
 x = np.arange(len(y))
 fittedParameters, pcov = curve_fit(func, x, y)
 y_fit = func(x, *fittedParameters)
@@ -64,10 +66,11 @@ axs[0].plot(x, y_fit, 'k:')
 
 axs[1].set_title('5 initial prey')
 # axs[1].set_ylabel('Herding Ratio')
-axs[1].set_xlabel(r'Initial predator survival time t $\times$ 100')
+axs[1].set_xlabel(r'Initial predator survival time t $\times$ 100', fontsize=11)
 x = [str(int(x[1:]) // 100) for x in i5_p150[0]]
 y = [x[0] for x in i5_p150[1]]
-axs[1].bar(x, y, color='#009440')
+# axs[1].bar(x, y, color='#009440')
+axs[1].bar(x, y, color=col1)
 x = np.arange(len(y))
 fittedParameters, pcov = curve_fit(func, x, y)
 y_fit = func(x, *fittedParameters)
@@ -75,10 +78,11 @@ axs[1].plot(x, y_fit, 'k:')
 
 axs[2].set_title('2 initial prey')
 # axs[2].set_ylabel('Herding Ratio')
-axs[2].set_xlabel(r'Initial predator survival time t $\times$ 100')
+axs[2].set_xlabel(r'Initial predator survival time t $\times$ 100', fontsize=11)
[…]

### 2021-05-01 plots/gen_inn_last_fish_pop_chart.py

@@ -2,6 +2,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import pickle
 import matplotlib as mpl
+from lib import col1, col2, col3
 
 
 mpl.font_manager._rebuild()
@@ -23,12 +24,15 @@ print(len(a))
 
 fig = plt.figure(figsize=(4, 3))
 plt.plot(a, linewidth=.8, c='#ffffff')
-plt.ylabel('Prey population at the end of an episode')
-plt.xlabel('Steps in million')
+plt.ylabel('Prey population at the end of an episode', fontsize=10)
+plt.xlabel('Steps in million', fontsize=11)
 plt.xticks([0, 2000, 4000, 6000, 8000, 10000, 12000, 13980], ['0', '3', '6', '9', '12', '15', '18', '21'])
-plt.axvspan(0, 2000, facecolor='#00622c', alpha=1.0)
-plt.axvspan(2000, 4800, facecolor='#007a35', alpha=1.0)
-plt.axvspan(4800, 13980, facecolor='#009440', alpha=1.0)
+# plt.axvspan(0, 2000, facecolor='#00622c', alpha=1.0)
+# plt.axvspan(2000, 4800, facecolor='#007a35', alpha=1.0)
+# plt.axvspan(4800, 13980, facecolor='#009440', alpha=1.0)
+plt.axvspan(0, 2000, facecolor=col3, alpha=1.0)
+plt.axvspan(2000, 4800, facecolor=col1, alpha=1.0)
+plt.axvspan(4800, 13980, facecolor=col2, alpha=1.0)
 plt.axvline(2000, color='black', linestyle='--' , linewidth=.2)
 plt.axvline(4800, color='black', linestyle='--', linewidth=.2)
 plt.axhline(2, color='black', linestyle='--', linewidth=.5)

### 2021-05-01 plots/gen_swarm_comp_chart.py

@@ -198,11 +198,16 @@ def plot(data, err_data, data2, err_data2, xxx=30):
     custom_handler2.set_image(os.getcwd() + "/fishpop.png", image_stretch=(-2, 11), special=True)
     p1 = mpatches.Patch()
     p2 = mpatches.Patch()
-    ax.legend([*bars, p1, p2], [*data_keys, 'Prey caught', 'Left-over prey'], handler_map={p1: custom_handler1, p2: custom_handler2})
+    ax.legend(
+        [*bars, p1, p2],
+        [*data_keys, 'Prey caught', 'Left-over prey'],
+        handler_map={p1: custom_handler1, p2: custom_handler2},
+        fontsize=11
+    )
 
     plt.xticks([0, 1, 2], scenarios)
-    plt.xlabel('Algorithm')
-    plt.ylabel(r'Sustainability $\sigma$')
+    plt.xlabel('Algorithm', fontsize=12)
+    plt.ylabel(r'Sustainability $\sigma$', fontsize=12)
     plt.xlim(-0.5, 2.5)
     plt.tight_layout()
     plt.show()

### 2021-05-01 plots/lib.py

@@ -37,3 +37,8 @@ cmap_mod = truncate_colormap2(cmap_mod, minval=-.2, maxval=.9)
 # cmap_mod = cmap_mod(np.arange(cmap_mod.N))
 # cmap_mod[:, -1] = .95  # np.linspace(0, 1, n)
 # cmap_mod = ListedColormap(cmap_mod)
+print(cmap_mod(179))
+cutoff = .55
+col1 = cmap_mod(179)  # #37669e
+col2 = cmap_mod(159)
+col3 = cmap_mod(199)
